\documentclass[ebook, 10pt, openright, onecolumn]{memoir}
\usepackage[LGR,T1]{fontenc}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[final]{microtype}
\usepackage{todonotes}
\title{On the Verge of Poor}
\author{Tyler Thomas}

\setlrmarginsandblock{0.15\paperwidth}{*}{1} % Left and right margin
\setulmarginsandblock{0.2\paperwidth}{*}{1}  % Upper and lower margin
\checkandfixthelayout

\def\signed #1{{\leavevmode\unskip\nobreak\hfil\penalty50\hskip2em
  \hbox{}\nobreak\hfil(#1)%
  \parfillskip=0pt \finalhyphendemerits=0 \endgraf}}

\newsavebox\mybox
\newenvironment{aquote}[1]
  {\savebox\mybox{#1}\begin{quote}}
  {\signed{\usebox\mybox}\end{quote}}

\newcommand{\textgreek}[1]{\begingroup\fontencoding{LGR}\selectfont#1\endgroup}

\newlength{\drop}
%% specify the Webomints family
\newcommand*{\wb}[2]{\fontsize{#1}{#2}\usefont{U}{webo}{xl}{n}}
%% select a (FontSite) font by its font family ID
\newcommand*{\FSfont}[1]{\fontencoding{T1}\fontfamily{#1}\selectfont}
%% if you don’t have the FontSite fonts either \renewcommand*{\FSfont}[1]{}
%% or use your own choice of family.
%% select a (TeX Font) font by its font family ID
\newcommand*{\TXfont}[1]{\fontencoding{T1}\fontfamily{#1}\selectfont}
%% Generic publisher’s logo
\newcommand*{\plogo}{\fbox{$\mathcal{T}$}}

\newcommand*\td[1]{
  \todo[inline]{
     #1 
  }
}


%% Define some commands for marking up the chapters 
\newcommand*\starbreak{\fancybreak*{\Large{* * *}}}
\newcommand*\finish{\td{ ----- Finish this section -----}}

\newenvironment{poetry}
{
  \begin{quote}
    \begin{itshape}
      \small
    }
    {
    \end{itshape}
  \end{quote}
}


\newcommand*{\titleAT}{\begingroup  % Anatomy of a Typeface
  \thispagestyle{empty}
  \FSfont{5bp} % FontSite Bergamo (Bembo)
  \drop=0.1\textheight
  \vspace*{\drop}
  \rule{\textwidth}{1pt}\par
  \vspace{2pt}\vspace{-\baselineskip}
  \rule{\textwidth}{0.4pt}\par
  \vspace{0.5\drop}
  \centering
  {\FSfont{5ml} % FontSite Mona Lisa
    \Huge ON THE VERGE OF POOR}\\[0.5\baselineskip]
  {\FSfont{5ml}
    \Large a memoir}\par
  \vspace{0.25\drop}
  \rule{0.3\textwidth}{0.4pt}\par
  \vspace{\drop}
  {\Large \scshape Tyler Thomas}\par
  \vfill
  {\large\scshape $T^2$ Press}\par
  \vspace*{\drop}
  \endgroup
}


%% At some point kill the chapter numbering in this pagestyle
\addtopsmarks{headings}{}{
  \createmark{chapter}{both}{shownumber}{}{. \ }
}
\pagestyle{headings}

\let\cleardoublepage\clearpage

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                     BEGIN DOCUMENT                    %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\pagestyle{headings}
\titleAT
\clearpage

\frontmatter

\null\vfill

\begin{flushleft}
  \textit{On the Verge of Poor}

  © COPYRIGHT Tyler Thomas

  2019
  
  ISBN--INFO

  ISBN--13: 
  \bigskip

  ALL RIGHTS RESERVED  
\end{flushleft}

\clearpage
\tableofcontents
\clearpage

\mainmatter

\chapter{Prelude}
\label{cha:prelude}
\begin{aquote}{Latex Memoir Class Documentation}
  \textbf{memoir}, \textit{n.} a fiction designed to flatter the subject and to
  impress the reader.
\end{aquote}

The rain patters outside and I stare out and across the world to a place
somewhere I left behind, not in dismay at my leaving, but in awe of a timeline
which I can call my own but which has no place in the now.  There are only
memories, moments floating across the inside of my eyes, some shadowy
self-conception that will for a instant crystallize to definition, and then fade
back into the veil as through a glass darkly.

We all make up stories, some just more blatantly than others.  Some small thread
we will grab and pull, pull till out of this single line the fabric of our life
can be so neatly unwound and all that is left is a little messy pile of dreams
from the past, yarns told to our children before time erases even those.  Are
these tales for us or for them?  Is it some grasping at ourselves in the mirror,
an attempt to make sure we are truly choate, or are they merely one long excuse,
we standing athwart history and yelling, ``Wait, let me explain!''

There is some guilt in our existence always, the primordial debt we can never
quite repay, and so we leave off looking at what we have made of ourselves.  And
yet here I sit, stumped at a story which should come as second nature, all
explanations and maudlin interludes.  Maybe I have not yet begun to look, but am
still just peeking though my fingers and constructing stories from shadows on
the wall.

Oh, but how those shadows dance so well...

\chapter{Desert}
\label{cha:desert}

\begin{poetry}
  Stark skies breathed in vains\\
  in arroyos lost amain \\
  upon a skittish horizon
  
  It was a day, a year, a decade gone\\
  I tramped the trails of heat and land\\
  My feet would beat this tattoo into the sand\\
  into the still I still hold in hand\\
  and give to grace the morrow

  In the world's calvous hide\\
  I find, I lie\\
  I try to abide the stasis wrought\\
  the solitary dream of gods\\
  and beasts astride\\
  the lip of creation

  Whensoever this rident plane\\
  I laugh back fulsome distain\\
  for the heavens who keep the rimpled rain\\
  tucked in the smell of tomorrow
\end{poetry}

I remember the desert most.  Days of walking down roads which led nowhere in the
hot sand and silence, my form of nihilism.  Whole days I would be gone, starting
in the comparative cool of the morning and returning as the sun set over a flat
horizon an incomparable distance away.  After school, after work, on the
weekends I would always seem to wander off a bit farther, never wanting to turn
back.  I would walk with water always, big jugs that I would lug along which
would start with ice and slowly warm to tepid, and then the hot before I could
quaff enough to sate the heat which dripped down my legs and dried crisp and
salty on my neck.  Yet it didn't matter.  Nothing mattered out there except to
keep going, to stay in motion for its own sake.  There was nothing else to do.
Walking was meditation, a activity to involve nothing but that one action in the
legs.  It was a escape in slow motion.  In the desert one could think and feel
and contemplate, and it was at the same time the irrelevance of the quotidian in
the silence and stillness of the terrain.  

Casting out into this distances in some omphalocentric perambulation, I always
arrive back where I begun both in mind and body, back at my house, an old single
wide trailer with wall of faded and broken paneling and a roof with tires on the
top for a reason I never knew and never asked.  We had torn all the carpeting
out when we moved in and painted a giant ill-formed bird on the living room
floor, everything else blue because that was some paint we had. The front door,
glued two-by-sixes, faced a view miles in size, and I would stand on the
creaking gray wooden porch and contemplate the mountains distant, ever inviting
me to their feet for no purpose.

The first landmark that one would find after leaving down the dirt road which
stretched out from home was a dirt damn known as \textit{the pond}.  This
purported `pond' usually was devoid of water and instead just a dry brown basin
to stand as emblem of the constant aridity of the landscape.  When the rains
would finally come first hesitantly, then completely, myriad arroyos would fill
the pond with a fragrant brown liquid still foamy after its hurried course.  And
suddenly a life hidden beneath the mud would emerge in the form of a million
frogs whose frenzied calls could be heard through the walls at night.  It was
the sound of a life-cycle, the hurried croaking in the dark while the water
drained away till only tadpoles remained frozen in clay, fossils which would
fade in days and then be gone with no trace of the life dug beneath the baked
earth.  A vast system of scales would appear where once water had been, and dry
till each crack curled upward and detached like sun-burnt skin, a flaky sea
that crunched underfoot.

That pond has always stuck with me, this one symbol of the desert, of my
childhood taking the dogs out walking, our big lumbering dog named Spike and her
tiny Chihuahua companion running hard by her side.  Spike would disappear for
hours and finally return home panting dirty with some adventure that only she
would ever know, dirt and strange smells clinging to her sides.  Later I would
go dove hunting out at that same pond, hiding in the bushes on the side, or
ranging further in search of rabbits.

Beyond the pond lay The Big Arroyo as we called it.  This formed the meeting
point of many smaller channels streaming down from jagged peaks of the Organ
mountains to the east.  After the rain, it would fill and become a roaring river
for half a day taking rocks and bushes to some resting place I would never see.
I would ride my bike to the top of the hill where the road intersected this
nascent river, and steeling myself attempt to come crashing down the hill and
into the swirling currents, pushing the peddles as hard as I could to get to the
other side while grass and twigs strained themselves into my spokes and slowed
my tires.  If the current was to strong, I would find myself holding with one
hand to my bike as we both were taken down the stream and trying to struggle to
the side.

The Organ mountains were the orientation of everything, establishing direction
in a land flat.  I once climbed over these mountains starting from my front
door, half a day gone in reaching them, the rest to scramble up the cliffs and
down the other side.  I thought I could return in the day still, but ended
instead sleeping astride the mountain's saddle next to a smoky little fire while
I shivered at its side.  I finally came home to a search party come from all
around to save me, myself sunburned and dirty wandering up to see what all the
fuss was about.  I still remember my mother come running out of the front door
to hug me and make sure I was in one piece still.

\finish

I had come here as a newly turned teen after a stint in Denver.  I had taken up
fly fishing and paid for my gear with the money.  PBS had a show on every
evening called \textit{Fly Tying: The Angler's Art} which I would watch
religiously, each day setting up my gear on a TV tray and trying to follow along
with all that the host did.  I remember being so enthralled by such a quiet
art.  There was some captive calm in each of the hosts which would endear me to
those moments even to this day.  It had the quality of Mr. Roger's Neighborhood,
a soothing to one's childhood sole.

Before Denver there was a stint in a town sat in the middle of southern New
Mexico called Truth of Consequences.  My mom had bought a house up on the hill
overlooking town where we were to live for half a decade while I awaited my
transformation into an adolescent.  Having picked up a book on paper airplanes
at a library sale, I at once became quite obsessed with the art and would spend
hours making paper airplanes of a complexity which would even now amaze me.
Each airplane would require several sheets of paper and much patience measuring
out the many constituent rectangles which would then be folded and glued in a
myriad different shapes to construct a left wing with one, then a right with
another.  The tail was made of several peaces to be all glued into place.  After
each of these were cut, glued, colored, and assembled, a cockpit would then be
folded into a three dimensional form which would slide into place last of all.
All this would then be test weighted with bits of paper clips then glued into
the fuselage as a final step.

At one point I had gone so far as to organize a paper airplane contest for the
neighborhood kids, a motley collection of the product of broken homes.  At my
age, there was little comparison to be drawn, but looking back now at our little
strange neighborhood, I can only half laugh at the quality of our little
community there atop the hill on the edge of town.

My sister was born there, a small little funny creature which I made my play
thing.  I would create elaborate scenes of stuffed animals and pillows around
her as she sat un-understanding but amused.  At some point I went so far as to
sow her a ninja outfit with probably the assistance of someone.  It was a purple
silk affair that she would wear at my behest as she crawled around to my
satisfaction.

One again here we had found our self on the edge of development, the backyard
butting up to the undeveloped desert.  After a dirt road the ground fell a good
ways till one found the floor of the desert at its natural height.  For some
reason there was an extruded bit of land like a peninsula left by the developers
who had set the whole neighborhood flat.  This became some locus of play during
the course of our time there with all my friends and I drawn there for reasons I
cannot now recall.  It was on the edge of the unknown and the known, we standing
there like Columbus upon his ships bow on the edge of a primitive landscape
uncultivated by humankind.

My mom did not make it long there, instead selling a house still mostly owned by the
bank and moving to Denver to live with my grandmother for a tide.  We would
all cram into a small house with two bedrooms, we all cozy and cramped while my
mom figured out the next stage.

This would come when we once more packed up and moved south, this time to Las
Cruces where I would spend the remnant of my adolescence and from where I would
move off to college six years later.  

Memory is odd when called again from places so far removed from the moment.
What truths do I have of this time, and what is just the silt of time gathering
amongst theses small flashes, expanding them until I have again a feeling for
the time and the age made from  small accretions throughout all the years
since.  Timelines bleed into each other and overlay intents and interests.  How
is it that we can ever call ourselves again from the past without merely
remaking something prior into something present?

I try to become myself at that moment, but know not how to begin.  How can I
forget all that I have come to understand in the decades that have passed?  I
write this out twenty years removed and wonder what it was to be myself with so
little reference to anything.  I'm sure in another half century I will ask the
same thing of the present, the weird wharf and woof of the years twisting time
deeper into my bones.  We all are hunched with the weight of the years in the
end, bent in our memories and regrets and less and less attached to the present.

\starbreak

I could often be found next door digging up my uncle's yard, uprooting mesquite
bushes, battling their spines, reworking the land to something less than wild.
My uncle and I had a struck a deal in which he would pay for my first computer
(a Gateway machine with a 10G hard-drive, a CD burner, a floppy drive, and a
dial-up modem) and I would landscape his yard at five dollars an hour over the
next year.  This was the point that I really fell into my life-long love of
computers.  I remember when I discovered the brilliant way in which a web page
worked, the systematic markup and the intricate way that everything came
together.  To think in the way that a computer thinks is to contort one's mind
into the ultimate systematic methodology of deconstructing problems.  These
problems are defined well enough on the computer, small microcosms with fixed
inputs and fixed outputs.  Yet, this type of thinking is something which will
scale upward also, structuring the ways that one thinks about more complex
aspects of nature.  I am always interested in the lack of overlap between
computer scientists and philosophers, as both seem to reinforce each other. To
my knowledge, the only philosopher of note has been Mencius Moldbug, computer
scientist and radical political theorist.  

\finish

Seven years I was home-schooled before I had taken the plunged and gone back to
public high-school starting freshman year.  It was a year of great angst and
exploration, this the first great Individuation from the outside.  Life prior
had been one familial, that of cousins and uncles primarily outside the nucleus
of mother and sister.  I would ramble between houses and desert, video games and
22 caliber rifles.  The heat was always present, a dry baking in the sun, in the
sand, a brief reprieve of the pool or a sprinkler till once again the dry heat
held me.  All this was my world till I turned fourteen and it opened to a whole
host of divergent lives which came and went in intersecting spirals.  The
cousins had all faded, all graduated or moved away, the diffusion of life in
full force.

I met Tony sitting on the floor in an indoor basketball court.  This was Phys
Ed, that awkward required class that all had to finally give themselves to, very
few willingly.  Tony, a strapping Irish boy just transferred sat on the floor
next to me. This was the part of the class that our body-building teacher failed
to learn the limits of the average high school student.  We did another set of
push-ups. Between sets, looking at my long hair and plaid attire standard at the
time, Tony's first words were, ``Hey\ldots hippy!''.  And thus began a strange
friendship.

Tony was less person than smirk.  He wold saddle up next to you and give that
laughing fist bump like you were in on a joke he was about to tell.  You were
being cultivated.  Tony's great joke was that he was always busy pulling
everyone inward, befriending all those in his orbit, charming each with the
comfort of his own skin.  Good looking, well built, he would work his bad-boy
shtick, the relaxed nihilism our age craves.

He would be no Good Boy.  Foster care at an early, he had floated between
houses, between moms, between other people's lives.  He had landed with a family
consummately middle class, a dog and no kids of their own.  Terry took them as
they where, well-intentioned and somewhat naive.  They would have him as that
nice middle class son, a set piece in their lives, a good son.  Yet real mom had
always told him, scolded him, yelled he was a bad boy.  Then came his new moms.
They kept packing him off to someone else, into someone other life, he never the
right boy, that good boy. 

And so he became the bad boy once more.  In the ferment of post-pubescent youth,
there is a draw to the rebel, a rejection of the order one has really never
known, a check he could now cash against his childhood.  To be an antinomian was
to have the ultimate individuation, to throw off even the society.  Everyone
wishes to be their own Napoleon and never realizes they are only a Raskolnikov
breaking something just to see what will happen. He was that fun force of chaos
that pulls inward like a black hole, everyone falling into Tony and his thrills.

\td{Rework all of this section}

Dropping out of school he took to check fraud after one day receiving a box of
checks in the mail addressed to a past tenant.  This was not his apartment, but
just that of a friend who let him stay. He would always find someone to let him
stay, inhabit there living room, eat their food and do their drugs and remake
their world into something like a nexus for all the traffic of Tony's life, he
the spider who had so craftily spun this web of people who came in pilgrimage
now.  He was the orchestrator, the center of this universe of people and
connections that flowed around him, bringing him all the things he needed or
wanted.  For years he rode couches and rode friends till the cops came and
kicked everyone out, leaving Tony always and somehow to escape and find a new
hole to squirrel himself into.  He was always fine --- till one day he wasn't.
Walking out of a gas station, a squad car awaited him.  Later he would learn
the man checking out before him was someone he had forged a check with weeks
before.  Tony had forgotten, but the man hadn't.  Tony spent my senior year in
jail.

\starbreak

Snider and I would sometimes skip school, escape the days expectations and
instead drive out into that still desert.  One of us always had pot stashed
among our things somewhere, a smelly sandwich bag hidden and a pipe in the glove
box. We would smoke and laugh and hackysack and hackysack for hours, circling
each other like pugilists, making trails in the dirt as this tiny ball the only
point of contact.  Finally hunger and pain would drive us from our trance and
back to my house and the world once more.  I would make a skillet overflowing
with stacked red enchiladas, refried pintos, top in lettuce and tomatoes and
sided with chips and toast with honey.  We would feast till we were both sated
and unmovable and contemplate our day and try to forget the morrow.

Other nights we would go scavenge wood from creosotes, build our little
stash into a fire and sit the night around with Old English 40s and laugh and
yell and scavenge more wood in the dark till we gave it all up and unrolled our
sleeping bags under a sky whose horizon was only where stars ceased to be, and
stayed the night in the open air and dreams of nothing.  The morning was always
gray in our haze with not a cloud in the sky.  The dust was in our hair and the
smell of smoke in our clothes, the night prior now memories and the future was
always crashing towards us still.

Then there was Jessica. Jessica and her tits.  She would pull them out at all
times, the young man's totem, huge and hanging like planets.  Pink pillowy
things with areolae bumpy and stretched, she would hike up he shirt and display
them for all occasions.  She would show strangers in cars next to ours, to
pedestrians, to anyone who looked interested.  We would all wait expectantly to
see when the time was right, when was the next showing. Then out they would
come, and all laughing we would secretly congratulate ourselves for something
not understandable.

One night she masturbated in my back seat while I drove down a road spotted in
street lights, Tony riding shotgun and smoking.  Light and dark would
alternatively show her face twisted in my rear-view mirror, moans from the dark
for a minute and then her eyes.  Tony and I were quiet, neither of us knew what
to do.  ``Are we almost there?'', she asked casually when she was done.

\starbreak



High-school is the age which one can still be said to have ``promise'', some
mystical check to cash in the future.  My life rode two parallel paths, one of
promise, and one of dissolution.  I fought the last semester for an extra
Advanced Placement class, a fifth college-level chemistry instead of a standard
four class semester, or the two classes I needed to graduate. This is called,
``being an over-achiever.''  Yet, my days were often still spent in debauch, in
search of the good time of drugs and dissipation.  The last two years I would
come to class high most mornings having not done my homework.  I made no
apologies, took zeros on the work and got As on tests, and generally acted like
I didn't care a whole lot.  I had always harbored a secret comfort of being
certain I was the smartest student in most rooms I entered.  To ensure I never
had to test the issue, I held my grades lightly, uncaringly as a shield.

The economies of public schools are so very different from their purported
mission.  Those who are good at learning the material of which most classes
consist is something disincentivized by the majority of one's peers.  And this
is the paradox, the difference that one must always split between that of the
peer-group, and then that of the institution.  My game was to play both sides of
the field, to be both the rebel and the scholar.  To find approbation on both
sides and not have to choose.

Was it this that led to the great discovery of my youth, that I had to break all
molds if I was to not be found lacking in some metric.  I would break the
meter, reform the measurements, and by this I would avoid judgment, for to what
standard could I be held?

\finish{}

I got a job working in a Mail Boxes Etc my Sophomore year and worked the job
till I graduated.  The job was easy, sort some mail, run some postage, and run
the counter.  My aunt had introduced me to the owner, Ray, something of an old
hand at most things.  He was a machine gunner in Vietnam, champion weightlifter
in the army, and general cowboy.  He had worked for the oil company ran his own
businesses, and told stories sometimes about dating a stripper in Texas.  Now he
was running a little mailing store and dreaming about retirement.  He would roll
in with his new shiny car, perpetual cigarette hanging limply, and start playing
solitaire on the computer.  After surviving the jungles in Southeast Asia, he
didn't take anything too seriously these days, instead taking life as it came.

I would work after school most days of the week, a few hours every day before
the store closed up.  On weekends I would run the place by myself most days,
just me and the mail, building boxes and printing labels. Ray would pop in at
close, grab the money from the envelope hidden in the back after I counted
everything down twice, and we would head out for our weekend.

The store folded my senior year, the place not pulling in enough business after
the grocery store next door closed down.  Russ move on to a few more gigs before
retiring to a farm and a bunch of horses who now take up all his time.  The end
of a long life of adventure was the calm of a horse trotting beneath him, only
the desert spreading in all directions.

\finish

The years disappeared as the are wont to do, and senior year came rolling
around.  Tony was gone, Jessica moved away and only Snider and I still played
hackysack in the desert.  Things and friends shift strangely in ways subtle,
such that those who were close now seem far, and suddenly new faces appear to
frame your memories.  This year was different, I was going to college soon,
somehow I need to get my life in order.  One day I had dumped out all my pot
while walking in the desert and buried my pipe in the sand at a place to remote
and unremarkable to ever find again.  The desert is amazing for allowing things
to disappear, the hot sand returning to its level as if unmoved for an
eternity.

\finish{}

The three of them walked in to my chemistry class together.  Had they all met
before, or was it now that they where just drawn to each other? Nga and Nhi were
both from Vietnam, quiet girls demurring. Then Anja, from Thailand.

Anja had a charm probably known as spunk, some confidence I could never quite
find even if I tried to fake it. She knew only to act, not to think too much
about that action.  After me reciting the contours of a fear I had, she would
respond, ``So! Just do it'', and I know this no hyperbole.

There was something so attractive about her difference, about the
incomprehensibility of the foreign.  I would sometimes look at her askance and
think her another species, something superior, something pristine and yet
hardened to life in a way impossible to me.  She was this thing from the outside
which came here of her own accord from across the globe, from a life I would
never understand, from a place too different to comprehend.   

\finish



I had fallen for the first time, a puppy love maybe, something too hard to
analyze even with words for categories.  Snider and I were riding back one
night, and I, high and sleepy, sat shotgun concentrating my whole desire, my
whole being on trying to manifest Anja's presents right then, right there.  To
have her sit with me in that moment, and feel her warmth and her breath, to know
her somehow made solid with my touch, that I could make choate this emptiness by
the sheer force of desire.  Even today I remember that moment so distinctly, all
my will focused on the one thing least available to its force.

I closed my eyes to my dreams and the car hummed as we plied the way home,
Snider and I both quiet, lost to our fictions and dreams of a world not the one
we inhabited.  It was not long after she left again for Thailand, for her family
and her career.  Now she is a doctor, married to another doctor and both in
love, both the right fit.  Everything is right in her life, she happy and
content, and I am happy for her half a world away.

\starbreak

Prom night my Junior year, the triad of Tony, Snider and I decide it was time
instead for a boys night, a protest against our being single.  We would instead
take the night by storm and have a party our own.  There are certain dates which
are tyrannical in their implicit expectation.  As much as the idea is denounced
or the holiday derided, the lack of a feeling, an experience, is felt a loss
nonetheless.  It is to be sad for something one wants not to want.  Being alone
on December 25th will always feel a magnitude more empty than any other day; and
the same is true of those who try and deny Prom its due.

We had passed money to the right person and ended with alcohol, a thing
difficult to obtain normally.  After having scoured the town for parties, for
things interesting and coming up short, we decided to go visit Paul who lived in
the Porta-Potty at the park.

The three of us had met Paul a month prior.  After a good hack session going
late into the night, Tony took leave to relieve himself by visiting the line of
Porta-Potties set shoddily at the edge of the parking lot, the solution to a
broken bathrooms never repaired.  Tony, having approached the largest of the
lot, one made for the possibly disabled or the odd family, threw open the door
and started in only to be standing approximately on top of someone sleeping on
the floor.  After both had let out the appropriate expletive laden sounds, with
Tony having retreaded a good several yards in a motion not unlike teleportation,
everyone stopped to take stock of what had just happened.  The commotion had
brought myself and Snider over to have a look.  Tony gave us a recap of having
just kicked a man lying on the floor of the blue toilet, and after a strained
laugh, we conferenced as to what to do?  Was the guy drunk?  Was he dying?  Why
was he there?  ``Well, better ask'', Tony decided for the lot of us, and once
more approaching the potty knocked gently and bid the inhabitant a questioning
hello.  The response was normal enough for a man found sleeping in a park in an
extra-large portable toilet.  He even was nice enough to open the door after a
strained exchange of greetings and we came to know his name as Paul.

Paul was a man that looked like life hadn't given him a good day for a decade or
more.  Wearing dirty stain sweatpants and turtleneck fashionable for the 50s, he
told us of himself.  A man more in body than in mind, he seemed in a cycle of
the street.  His last attempt to find four walls not of plastic ended when his
last check was mugged, leaving him again to return to his Porta-Potty.  A simple
man, torn to pieces by life, left to the vicissitudes un-understandable to a
mind like his. Not only was it his mind, but also his body that had the worst of
it, with him missing a leg. Or such was what we assumed given his awkward gate
and the odd \textit{swoooshing} sound of a compressing hinge emanating from the
pants hiding his knee-like apparatus as he walked.  We bought him Taco Bell and
wished him well, for what else could we do?

Paul was the poor \textit{reprobatus} of some Calvinist deity, someone too low
in life to ever find a salvation.  These are the un-elect whom one feels helpless to
help, Paul floating in a world too far away to ever find his way back, in some unjust
judgment too hard for us to contest, too complicated for our own lives filled
already.  We drove away talking in low tones about how life can take a person to
such lows, unimaginable to us.  It was then that we decide on the one small
step, that one thing we could do for us as much as Paul, was to buy him a bungee
cord to keep his door closed at night.  The following day, we went on a mission
to the nearest home store to get this ersatz lock, gifting it to him with
several tacos and a twenty dollar bill.

It was to this Paul we now went with beer and pot and tacos in hand.  As it
turned out, Paul was nowhere to be found, and would never be found by us again.
We ate his Tacos and set up in the park anyway, ate and smoked and drank and
where happy in our youth and our debauch.

\chapter{Adobe}
\label{cha:adobe}

\begin{poetry}
  The smell of youth and striving\\
  a still ferment in silence\\
  I feel the roiling\\
  the mouth agape in static scream\\
  and I am restless to know.

  
  I would fondle all these thoughts\\
  my perversion, a porn of metaphysics\\ 
  I would make love in words\\
  twist a phrase so fine\\
  it could catch the quaver in the air\\
  and thrust hard into the stillness.


  I would touch your mind.\\
  I would split wide this tenuous tranquility.\\
\end{poetry}

I came to Santa Fe following the whiff of truth, subject to the oft-mistake of
those who find philosophy in the heat of youth; to think life really reducible
to a predicate logic like Russel's \textit{Principia}. It was only to follow it
out far enough, and in the end would emerge some shinning Truth to calm that
unnamed disquiet which pervades life before growing fully into one's skin.  It
cannot be there are no answers, only experimentation, only questions fraught
with unclear answers.  The tyranny of our freedom has yet to find us.  The
disgust at our fall still convicts us.  And so the sensitive end with Plato
under our arm and a question on our face.  We come with hat in hand to ask the
ages why and what and to please explain.

And thus I came to St Johns College, a little liberal arts college tucked into
the hills of the Rockies with the mountain Atalaya poking up from just beyond
campus, all adobe and curves and shrouded in Piñons.  The whole campus housed
about five-hundred kids from all over.  Each had come as character in some
vastly divergent story whose following chapter would be the little island of
Santa Fe in the midst of the desert, and the smaller still world of Johnnies
tucked into the folds of a time past. 

The curriculum was the History of Western Thought, a single major offered
on campus to all.  The whole of Freshmen class was to start with ancient Greek,
the grammar housed in some indecipherable tome which one learned to hate early.
Then there was math, Euclid's propositions devoid of number and only progressing
with the logic to build a castle of indecipherable ratios till one was left with
the Five Platonic Solids, and proof these were the only structures worthy of
divinity.  

It was the great homogenizing of Western thought before everything flew apart
into standpoints and the fracturing of reality.  This was the still naive last
stand at which one could still speak of things like truth as being more than
subjective.  Everyone came with hat-in-hand to the giants of the past and asked
in quiescent tones to be taught of things greater than one had ever understood.
Lived experience was of small value, for one had but a sliver of a shred to
speak from, and everyone was to be continually reminded of the ignorance of all
things that one must fight for the remainder of days given such a ephemeral
flesh.

The West as we knew it was a project constructed over millennia in a slow
accretion of excellence that would skip entire generations sometimes before once
again a spark would pull civilization along into a new epoch.  This was our
history, a discourse between the two sides of every man, one still the beast of
the field and subject to all emotions undifferentiated and engulfing.  The other
promises a purity, the world distilled into something inchoate and more pure
than any facet of experience embodied.  We all looked at once to the
\textgreek{ὃ οὐ κινούμενον κινεῖ} while still mired in ourselves and conscious
of a \textgreek{ψυχή} shared by a taxonomy whose branches are still minuscule. 

An epistemic humility was always the rule on campus, a reaffirmation every time
one opened a book written at a time considered barbaric, yet had sentences so
pregnant with portent upon the human experience that one was forever taken
aback.  This was a refrain which would structure the totality the time one spent
here, each year in the steps of the most brilliant minds all attempting to undo
the conviction of truth learned just the year before.  Philosophy is an example
of Kuhn's revolutions more than that of a continual construct.  Each generation
of philosophers first raze the axioms of the age come before and then
reconstruct new axioms on the ashes still smoldering.  Every major author was as
much a profit of destruction as construction, pulling society first into
question before again into dogma.

And so one would spent the years left only in the end with questions.  The
answers had long ago lost all conviction and instead something like Pyrrhonism
had taken its place.  Freshman year an \textgreek{ἀρετή} club was organized.  By
senior year, one would laugh at all that certainty and instead be left with only
Nietzsche and an attempt to understand at least the temporally of our
assumptions.

This could not be Nihilism though, for we all still would look to some remake
meaning, never as personal truth with would devolve into a maudlin simplicity.
Yet Nietzsche gave us the world ``value'' and told us all how to wield this
word, a thing which has no pretense to truth, but still speaks to the
arbitrariness of what it means to live a life well.  And so we still must go in
search for this thing or attempt to conjure it out of unknowns while still
subject to the paradox of Plato's Theaetetus and the impossibility of such a
task.

This were all things I would discover later.  I still remember the oddity of
that first day though, rolling into town with a truck full of stuff that I had
assumed necessary and hauling it into a dorm room that I could yet believe mine.
There are distinct moments of individuation in life, some more profound than
others and this has to be one, when a space separate from home takes on the
attributes of its essence.  Self, it seems, is half mere \textit{différance}, a
space between oneself and one's parents which can never close.  There is something
natural about the worship of ancestors as in this way we are all a lineage of
suspended meaning to another whose text you are tied but can never quite
summarize.

This I arrived on campus still testing a discreet self built up the last
eighteen years.  I was to have a dorm on the second floor, a tiny space almost a
closet off the main room housing my roommate, a red-headed city boy from Seattle
named Roy who was always sure he's about to have a really good time.  Or at
least half the time, as Roy was two people I would come to discover one
disconcerting day.  One studious and well spoken, a paradigm of the mature young
man that is going places in life.  This was to be the Roy I would meet this day
and present himself each morning for the next fortnight.  The other Roy was
rather the embodiment of an overactive Id who would emerge not sporadically or
uncalled, but more released on schedule, yet never less authentic for having
been pre-planned.  The first face of Roy wore button up shirts and would
discourse on the art of life and love and all Troubadourian ideals.  The second
owned a Curious George costume as complete body suit and was out to cause havoc
in any and all ways possible.  Curious Roy was the irrepressible alter-ego
housed in that same skin and then comes crashing through a facade of maturity
when some strange haruspicy has deemed the time had come.  Yet both knew of each
other, and both approved.  Neither thought ill of the other and each respected
his sphere.  

Roy biography was an ideal for myself at the time, containing several chapters
of nonstandard stories.  Roy had grown up in some idyllic city in a place I
could not comprehend, a Seattle told to me in all glowing bits and filled with
the availability of adventure.  He had a good family who was well to do, and had
spent his last years in some haze of perfection he would later describe as
inconceivable.  Early he had taken to driving antique cars and cultivated an
aesthetic which would later be bastardized by hipsters and made abhorrent in its
insincerity.  Yet Roy had none of this even as he wore flannel always and smoked
rolled cigarettes with gusto.  He would tell me of a game he would play each
weekend with his friends called, ``Where do you want to wake up?'', and would
require they drive to some distant destination chosen almost arbitrarily, a
place picked more out of waning day than as an end in itself.  All over the
Pacific Northwest he had slept in his car or in a tent nearby, the roving sole
of someone who had only the necessity of new ground to tread always.  I had
surrounded myself with a selection of friend who only knew simplistic modes of
life, cycles of smoking pot and playing video games.  Even the girls come from
Southeast Asia I had spent so much time with were still products of a settled
civilization which had less of that restless American spirit which would make
one drive for hours to find a new bit of dirt on which to place a tent.  They
had all come to the States not for adventure, but as a step in some fixed schema
in which this fit securely.  Roy was instead an embodiment of motion, of that
ultimate American nature relentlessly restless.  

After graduating from high school Roy had gone to India, boarding a cargo boat
with a hundred dollar ticket and spending the next several months traveling by
train and subsumed in the consummate difference.  He would tell me of the
oddities, the lepers and beggars, the dirt and the sweat of a people still poor
but a billion strong.  He would always circle back to the stares, and the
strange feeling of a million eyes focused on him with no sense of the
inappropriate.

Coming back stateside, he set out on a new adventure and drove his 1954 Volvo
out of the Seattle and east on a road trip going nowhere, circumnavigating the
boarder of the country just to get a lay of the land. Sleeping in small town and
parking lots and always pushing on to the next place, he would tell melancholy
stories of nights spent alone in dirty motels watching TV and feeling alone in
the world.  There was something romantic even in this, the Romanticism still
around tales such as \textit{Down and Out in Paris and London} or Henry Millers
recollections.  Degradation has its own appeal that is hard to quantify but is
something I have never given up.  A strange Romanticism still surrounds the
likes of those who plumb the bottom of life in some interesting way, who are
willing to test the depth of civilization and maybe come back the worse for it.

Roy came to St Johns the next year still driving the same Volvo down from
Seattle, again a pilgrimage across bits of the US I have yet to tread.  He had
come with a few possessions unlike myself.  Each item though had a cultivated
aesthetic to it which would make it seem an absolute necessity to person.  Even
though he would rarely use the record player he had brought and set upon a stool
in the corner, somehow there needed to be that record player at the ready and in
range of Roy at all times.  The same was true of his old camera, an antiquated
block of a thing in an age where digital cameras were remaking photography. He
of course would also set along the wall a guitar stand and an old acoustic
beauty which I did not know enough about to appreciate at the time.  Yet even in
my ignorance I knew the necessity of having a guitar set in that exact spot
after I had come to know Roy. 

I met him sitting in our new dorm playing his guitar carelessly and already
completely integrated into his place while and I carried two old CRT monitors
through this room and set up an awkward programming paradise in my closet which
dominated the majority of my small space.  He looked on amused, both of us
wondering what we would have to say to each other, the mischief making
adventurer from Seattle and myself, the desert rat with too much of a tech
streak for this campus.  As it turned out, we both liked wine and books, and
this was enough, both of us becoming closer only through a third friend we would
both make later named Slater.

Slater was to be found down the hall a few doors and introduced himself to us
out front one day wearing his little plastic bicycle necklace which would
distinguish his style for the time I knew him.  He had come down from Pittsburgh
by bus so that he could bring his bike with him, and old Raleigh that he had
built up and was oddly reminiscent of the bike that I would build a few years
later when I had come to find the joy of cycling myself.

Slater grew up in Pittsburgh where he had already been a year to university for
mathematics, an odd calling for the rest of his comportment and only realized by
himself later.  Like my own experience, he had a mixed record in high-school,
sometimes excelling but only selectively.  Math was to him somehow amusing at
school, and he would diligently pursue this in excess while ignoring the rest of
his classes for sheer boredom.  I somehow never learned too much of his time
prior to St. John's, both of us somewhat guarded in our recollections for
reasons which neither one of us would tell the other.  He told me a few stories
of his days as a delivery man, driving nights for some pizza place all the while
sipping beer and finding life generally unsatisfactory.  He talk in his looping
dreamy tones of someone much less steady in life than the young man I met and
one I could not believe the same.  Life for Slater always seemed a pretty neat
affair, as though he really had nothing too much to worry about and just was
here to smile and see what happened next.  Discontent seemed little in his
disposition for the totality of the time I knew him, and forever wondered about
how so different a self could have existed in a period still so little past.

Slater and became good friends, he somehow providing a good glue which would
join the three of us, Roy, Slater, and I.  It was not as though we would form a
friendship indissoluble to this day, but for its moment, it seemed perfect.  It
was not long till this triune slipped back into the stream of history and we all
separated, but I still felt as though these few months solidified a part of
myself which I can still trace back even today.  

When I arrived, I had felt an imposture, somehow coming from a trailer to a
school filled with a different demographic then I had found prior.  It was not
that some select group of kids had come from money which I knew, but that I had
found a different outlook cultivated by cities and a movement I had never known.
I was surrounded now by peers from important families and whose progeny it seem
only right should study Liberal Arts and learn poetry like the dictum of John
Adams on the point of the Union, assuming that war and government would be
figured out by my generation and all that was left was to study the arts and
perfect some philosophy too metaphysical to ever be operative.  These where the
children who would question all the axioms of the American dream and pull from
so many strands I had never seen to create the most interesting of lives even at
this point.  I look back now and see the ways this was a formative time in my
life.

I had never realized how similar were all my high-school friends, as though the
city or state produced an odd homogeny within its youth that had left little
option for the future.  I had never questioned fully the possibilities, never
taken seriously that life could be lived at such variance with everything I had
been accustomed to.  Then I went away to college and immediately knew the myopic
world that I had inhabited. I remember the amazement I felt in the shear amount
of interesting people my own age, none of whom were lazy and degenerate nor
sheltered and socially awkward which seemed the two poles around which a
magnetic field drew all in my hometown.  The binary growing up seemed to split
those who where expending the best years of their life in that moment, having a
hell of a time in disintegration and unseriousness, or those who would walk the
straight and narrow till they had secured some job that would allow an easy life
to follow.  It was not till St. John's that I saw so many example those who had
made instead some synthesis out of what I had thought irreconcilable.

It is both a revelation and an hard realization to suddenly think oneself
stunted.  This was not to be the last time I would feel as though I had somehow
given myself a smaller world than I should really inhabit.


\starbreak

And so the year began, classes all week and the rest of the time spent trying to
stay afloat.  The methodology practiced at the collage was something akin to
trial by fire, piling an ever increasing number of books and essays upon each
student till the demands where unduly intense.  

I had invented a rotation, a routine which would take me from dorm to class to
mess hall to library and then back again to my dorm when midnight hit and all
were kicked out.  Morning would begin at 7:30 with a scramble to make it to
class on time.  After extricating myself from bed, a quick change of clothes and
a quick brush of my teeth and I was off, still waking as I approached class and
sat on one of the chairs surrounding a large wooden table.  The table would
slowly fill as the minutes ticked down towards the top of the hour, we all
sharing a sleepy look and an uncertainty as to our preparedness.  The ten or so
of us would all then turn serious as the clock hit eight, suddenly all becoming
something much more respectable than we felt a moment before.  We were now all
last names, Mr. and Ms. as we sat straighter in our chair.  It was never quite
fake, but a performative aspect of the whole experience made be blush a bit
after.  It was a test to the efficacy of assumptions.  We were all to be treated
as adults, and could we then rise to the occasion.  For a tide it was to be,
class an hour and a half that we all aped adulthood effectively.  Then the time
would be over, and we would revert to something less clear and prolix, instead
slang and a laxity in our locution.  This change was forever somehow too sudden
and often I found amusement in it's jarring effect.

After my first class there was still time to catch the remnants of breakfast in
the dining hall.  At this point, the place had dwindled to a few lone students
placed here and there, eating eggs which had been drying all morning till they
had turned to rubber.  The beans or sausage was forever approximate, a
recognizable shape more than a texture or taste.  Yet town was always too far
away, a place that required a car or bike and an investment in time which we all
lacked, and so we would shovel some indefinite substance into our mouth and move
on to the next class.

It was early in the year that I had become vegan.  Growing up, we had all been
something approximating vegetarian less in name than in act. Mom had always
harbored a disgust for uncooked meat, and a suspicion of any which purportedly
was that it still had some salmonella hidden in a fiber less than burnt black.
It was a rare and glorious event to get a slice of meat not Spam, the one
substance most unlike the animal from which it came and always precooked.
Looking back, the exception given Spam to house in violation of a heath food
regiment I did not even know was in reign till I was older is something of a
wonder to me.  Hot dogs and baloney were anathema, yet there was some remnant of
respect still accorded the oft eaten pan of scalloped potatoes and Spam.  It's
origin is somewhere in mom's childhood I never thought to question and needs no
justification I suppose.

And so a glissade into Veganism was fairly easy.  I had never been fond of milk
and only had really to contend with cheese as my one weakness.  Mexican food can
survive either the exclusion of cheese of or meat, but with neither the name
become less convincing.  New Mexican cuisine tends much more to the caseous than
the carnivorous.  The shibboleth of New Mexico was the question, ``Red or
green?'' which was the sauce to underlie a melting shell of cheese in most
cases.  This triad of two sauces and cheese was a trinity never to be broke
asunder.  How to bisect this from my palate now, how to construct an enchilada
or a burrito without this one ingredient as axiom?

I remember the mood of the time, the aspect of youth that wants to foist upon
the world some idealism, or to instead test oneself in ways which do the same.
One must test the possible at this age, and see where one stands in the end.
And so I became vegan as a small act of will against myself.  Symbolism is
always something more operative than ever admitted, and this was a moment of
my own.

Symbolism seems now to have become institutionalized and no longer guarded
against.  I wonder at the myriad means by which one now has to kowtow to an
abstruse affectation.  Sincerity seems to have gotten lost in the shuffle of
modernity and now we all just want to signal the correct set of gestures.
Ideologies have become more totalizing, containing the whole of life as religion
used to.  With our disposition to the divine lost, we only have politics left, a
secondary morality which has created a lingo all its own and requires we act
always in accordance.  The requirement to reference The Savior is lost, and in
its place we talk in coded word or progress, we eat kale or practice yoga.  All
things intersect and signal our station and our nascent tribe.

Was I to do this with veganism now? Was this something only of a battle of my
own will, a small act of abstention for the purpose of strengthening my own
indifference to the pleasures of the body?  Stoicism has a long history and is a
latent ideal in all of us, the ability to undo a reliance on our \textit{Id} to
inform each action.  This was not only the project of Zeno and Epicurus, but
Ataraxia extends to eastward to the Buddhists, in the states of Yogic trance and
in the act of total self-control of the Samurai who kill not in anger but only
in accordance with duty.

Or rather was Veganism something of a sop to some ideology that had hatched in
my head and had come to full fruition.  Looking back now, I remember how readily
one falls into a politics which conform to a milieu was came to inhabit without
question.  I had at the time a growing liberalism governed only by some vapid
sense that this was an expectation of my environment.  Veganism was some part of
this same impulse even if it could be well argued by the facts.  I would tell
all it was a act of defiance against the treatment of animals, which is a valid
rational I still believe; yet in my heart-of-hearts, I also knew the driving
motive less atavistic than ever I would admit.

And so after eating my plant-based breakfast, there was just enough time to make
it to my next class.  Each would have a different dynamic, and admixture of all
the personalities in a dialog only at times productive.  A maieutic methodology
has is some ways the means to engage people impossible in any other system, yet
at the same time, it is in the end a chaos of ill-informed opinions in desperate
need of someone to set the record straight as to what was even said.  So many
classes were spent just in a state of half-remembered haze while we argued about
the system even set out, the rule from which we were asked to expand upon.

I really wish I could once again experience my ineptitude at the time, the lack
of context that is so prevalent in all the student body.  At once I wish to hear
yet also worry about my ignorant interjections and how I now would cringe at their
ineptitude.  

\finish

Trader Joe's was a name unknown to me, a strange coastal store filled with food
I didn't understand.  Nick and I had stopped one day while tooting around town
in his Volvo.  We shared a boule torn and dipped deeply into a tub of hummus
while sitting in the parking lot in the crisp air of morning and I completely
content with the world.  

James, the lanky white boy with a mop of sandy hair was always on that damn
unicycle.  He was a communist, extolling Marx to anyone who would listen,
lecturing always on the \textit{prols} and class solidarity.  Class solidarity
on an elite liberal arts college would seem to be more bourgeoisie than we all
felt at the time, young kids still seemly subject to some power structure we
were figuring out how to be part of without our knowing it.  

He drove an old VW Bus perfectly restored and paint job pristine who everyone
was constantly offering to buy.  His response was a deep galloping laugh that
would erupt, sometimes at unexpected moments as though it even surprised him,
that giant Adam's apple bouncing up and down.  

Late enough on the Friday nights, inevitably the sounds of a desperate yelling
could be heard from some quarter of campus, him weaving around on the single
tire with a half-empty gallon jug to wine in one hand and the Communist
Manifesto in the other.  He belt aloud page after page while careening around
campus, never actually falling but forever a mere second away.

\starbreak

Rose lived downstairs with the girls, a strange sophomore who I would often meet
lying on a bench in the common area reading.  I would be out front hacking
furiously, finding the groove and really going for it, and there would be Rose,
lying on a bench reading, having found some \textit{ataraxia}.  She was quietly
irreverent, filled with these interesting quips I thought above me.  

I used to steal her pomegranates.  She would leave them on the windowsill to
ripen, a mere foot above the ground on her first floor dorm built have into the
hill.  I would pass by, taking a snaking way from class, in some mental reverie
and there would be her perfect pomegranates, lined up like soldiers, ripe
irresistible.  I would call her name, ``Rose!, Rose!'', and if no response, grab
the biggest one and abscond into the forest with it like some prize I had one.
It was only when the year was fading I fessed up, told her where her fruit had
gone all the while grinning.  We talked the rest of the day on my balcony, about
life, school, and all things, and she gave me a pomegranate willingly as parting
gift.  I never stole another.

Rose stayed at St Johns for six years, studying not only Greek but Sanskrit to
read the Eastern classics.  Now she is a Forest Ranger in Death Valley, riding
around in a space so big as to feel your finitude, the heavens never that high
or far.  I suppose that the end of all of philosophy if done with truth is to
escape to the desert and contemplate existence at its essence, at the point of
its origin, to find the \textit{axis mundi} at a place so sparse to exist is to
be monad. 

\starbreak

The beginning of break I had moved into a shed, living in the back of a house
across town, this small structure with no heating and only an extension cord run
through the door for power.  There were no windows, so if I wanted to see the
world outside, I would have to leave the door open to all the elements, good and
bad, cold and hot.  I put my computer on the floor and laid the sleeping bag
next to it and called it home.

I remember those cold morning sitting in the sun the door open, reading a book
on programming, dreaming about the future, of things not touched by my life
still small in the shed.  There is no universal metric for achievement, and this
is the bedeviling problem of life; one can construct things in an infinitude of
ways and none be called best.  There algorithm to sort the sole and find a
singular value, the answer.  

In the house lived a bunch of Deadheads, hippies who would live lives I would
never understand.  Some went to St Johns, some did not.  The Grateful Dead
played always, everyday, and at every chance.  The only break was the guy from
Mississippi who was played an amazing Banjo which would rule the house for a
minute before Jerry took back control.

\finish

In the middle of the year Roy disappeared. We had all gone for Winter break and
Nick didn't come back, instead off again around the US for a reason he could not
name.  There is something inextricably drawing about escape, just packing up and
leaving, gone.  It has no point but its negative, its lack of place, the nirvana
of snuffing out.

Slater moved into my dorm from down the hall and on we lived in some
philosophical distraction, we always reminiscing about the time when Roy was
still part of the triumvirate.  Some fluid set of subsidiary characters would
pass through my remaining time, yet none would have a lasting hold on my mind,
myself even at this time withdrawing already, making a conscious solipsism of my
world.  It was into books I would fall so fully at this time I had no time for
others.

Philosophy is already half escape, a disintegration into the realm of forms,
perfect ideas which can float above this fallen plane.  One must just turn to
face upward, to deny the quotidian vicissitudes and instead see mere
approximations of a perfection lost to the present.  This was my form of
annihilation, an extra-spatio escape tied only to a gnosis always almost yet
had.
\begin{poetry}
  Conceptio culpa\\
  Nasci Pena\\
  Labor Vita\\
  Necesse Mori
\end{poetry}
And thus Stoicism finds it's appeal in an Apollonian impulse to draw back from
life into some purity not given by a God, but instead clean with definition and
pristine categories.  Yet truth is indeed a woman as Nietzsche warned us, us who
would dissolve ourselves back into the Divine Mind.  We all come stammering and
pleading, only to end our attempted conquest alone with the messiness of life
still at our doorstep.

I would at great disdain pull myself out of my books and head to the cafeteria
to indulge my body, eating as though in a meditation and still lost in some
thought I was having a while ago about something I would assume profound.

The world of the young man is always one of extremes, of simplifications forged
in a lack of knowledge one assumes instead complete.  You combines in direct
proportion conviction and myopia, the philosophic impulse only hiding one
beneath the other.  Philosophy is still the promise that the world is indeed
simple enough for comprehension, quantification, and systematization and to
simplify the world to a schema.

Nights were spent holed up in the library in an upstairs study composed of a
grid of tables, four chairs each and containing a solitary lamp in the middle.
As the night came on, often all that would be visible is rows of small lamps
with darkness in between, barely legible books along the outer edge of the room
with  spines in myriad colors.  I would sit for hours up there with the
only sound that of rustling pages and the white noise of the air conditioning
continually blowing gently in the background from some vent I would never
discover.  The size of the square room was always hollow at this hour, the
tenebrous void around me like a celestial space yet always comforting and
enclosed in tomes whose title was illegible and unformed in title but still
containing some wisdom I was certain.

And then a break, a momentary reprieve from my studies and into the cold of
night on the balcony just on the edge of the room.  The two dark doors sat as a
window into another world which I would tread and stand looking out into the
forest only half visible as the tree tops disappeared into the whips of smoke
emanating from the rolled cigarette glowing orange as I inhaled.

These were moments of collapsed time.  I would sit and study writings scratched
millennia ago in a world I can only half fathom in a state of no-place, a spot
outside the timeline, only words and air vents and all else without form and
void like my future and the past and what awaits me in the morrow.

Life was patterned, cloistered, monkish.  Importunate cycles guiding my days,
each hour a small epicycle governed by its own rotations.  Day and nights with
Greek and Plato, systems of stars and planets all aligned in proposition.
Declensions arrayed amain on flashcards, each paradigm another trail, another
night lost in symbols ever strange, in meaning tangled around a world reticent
to millennia. 

Friday night Bacchus reined, he the head of our collective unburdening.  We
plied the common spaces with smoke and drink and argued Aristotle till time
overtook our sureties and all faded back into dorms to dream in ways abhorrent
to the daily logic.

Saturdays were slow regret of some specious virtue forgone for the revelry of
the night before.  It was to set the stage for Sunday, a seventh day Jubilee to
start again, to reaffirm resolve Stoic and inspired.  And thereafter all library
bound, we arranged ourselves with bent heads not in prayer but with books in
hand we would recite our vows to \textgreek{αλήθεια}.

Such is the bifurcation always, the reality of life reaching too far into one's
ideals.  Most people live lives dual, one part idealistic to the point of
religion, another the realist who knows humanity fallen, some unhouseled ape
crawled from Atchafalaya gasping and growing legs.

\chapter{Forest}
\label{cha:forest}

\begin{poetry}
  I cast forth to winds\\
  to float to dreams\\
  in eddies upward\\
  to find my bit of heaven\\
  airless in unbroken sound

  I gasp\\
  I cleave\\
  I deny descent its due\\
  and fail to fall\\
  and dance naked for the angels\\
  for life\\
  for hope\\
  for flailing for its own sake\\
  and for\\
  me.
  
  What hath I\\
  but hight and step\\
  and toes which loath to touch the ground

  I wish my way to cloud and light\\
  wish a world in which to wonder\\
  with long hair\\
  to follow my head around\\
\end{poetry}

To live in the forest is to know oneself not part of nature.  It is be sure the
universe has ends not for us.  Religion is waning in the West for a good
reason; when most of the world seems made to cater to our whims what is there to
remind us that we live only in a shell of our own creation.

I moved to the forest while patches of snow still stood brindling the
ground. Most of my possessions had been carted back down south with the help of
my mother, leaving only myself and an old forest-green army duffel bag which
dwarfed my frame as I struggled out of campus and into the forest to the North.

Santa Fe climbs only ever higher towards the peak of Atalaya, a 10,000 foot
mountain which pulls the whole city into a vertical, dripping down the side of
the Rockies. I would climb Atalaya in the hot summer days and sweat in the heat
till I reached the pines, their languid needles long enough to hide the sun.
The ground was red mostly, a deep hue that conjured the Southwest as some
archetypal place as much in mind as in local.

The forest begins first in Piñons, small shrubby trees with not even a trunk
standing straight, growing only in the elevations still part of the city.  Here
one still feels space, the trees too small to really enfold a person into the
landscape, the sky always too big. 

Then one moves upward and into ravines and out again, sandy soil and Piñon hulls
through veins of caliche, gray and yellow patches of hillside where the path has
been cut too deep. In the rain, these patches become slick as though oil were
poured on the path, slippery and impassable except by climbing rock to rock.
Then the trail out climbs the Piñons, giving way to Poderosas, big pines that
dominate the landscape at times, others withering to a forest of small stunted
trees born from seed scattered onto some hard hill open only to the elements
and set in rock and clay.  There were the places where one finds orientation, a
sudden break in the cloistering forest onto an escarpment for a moment before the
trail plunges back into a shaded way.

At first the trail would take inclines in iteration, one now and a reprieve
before the next, but soon the vertical was constant.  The climb was done bent
forward, my full backpack weighing heaver each step, my tilt ever more to
compensate.  Up the entwined ridges till they met in a final push to the top.
At this point, I would turn off the path and instead start down a hill each time
taking a different route to avoid any definition. I would weave downward jumping
rocks and brush till I hit the ravine and instead made this my guide, following
its course uphill.  The valley was narrow, a small concourse hidden between the
legs of a mountain a thousand feet still to its peak.  I trod this fold till the
valley opened just a hair, and there would be my hammock, army green and strung
between two trees invisible if not your objective.

I lived to leave no trace, so that I could pack and leave only a smooth bark
rubbed by rope where my hammock would sway in the breeze, myself tucked into two
sleeping bags inside one another, the hammock flaps drawn tight and tied
underneath to form a nightly cocoon.  This is to climb into the Gaia's womb,
soft and warm and yet the sound of the open silence so acute as to be untethered
from the temporal.

My hikes were half the time at night, the stars lightening the terrain just
enough to stumble forward by, a twilight world of a million other suns of some
alien calendar lost in a sea of night.  Light from eons ago, stars burned out
and collapsed into darkness and void from which even errant rays cannot stray.
On nights when the moon climbed full from behind Atalaya, it would come like day
on a different plane, the underside of earth mirrored and yet still twisted.  It
was the world in a hue alien and alone, myself always the only one plying the
silver ground to my hammock hung deep in the shadows of even this *sol
secundus*.

This small outpost in the Santa Fe National Forest I found and called my own was
but a bit stuff tucked in a set spot.  There is something liberating in the
lightness to which one can aspire, to a place which is no place, a non-home.  It
is to uproot an axis from which one has to revolve, and to instead float along
to where the moment pulls the universe around you.  It was as much to be at home
everywhere, all places equalized in their option. Now it is but for the
choosing.  

\finish

The question of the possible is so bound by episteme unseen the majority of the
time.  Cultures create systems so seamless that to find a gap is to have found
something brilliant, a pin of light leaking in from the unknown.  These are left
unusually only to those few who are pushed out not of their own will, but
because they where not quite ever in; these are the tramps and the vagabonds,
the addicts and the saints.  Then there are those few of choose, who wish to
experiment with life and cast aside all expectation and run headlong into some
unknown.  I would not call this finding the authentic as Sarte would, but
instead call it play.

The human is an amazingly adaptable beast.  The patterns of life necessary for
forest living are all in the end completely manageable.  One's days become
structured just as do all other lives.  There is an inversion which happens, the
hard things becoming easy and the easy becoming hard.  Water becomes something
precious, not had without a huge investment in time and effort.  Yet one has not
to worry about paying the water bill, or of the piping in the house, or of water
the plants in the yard.  Now the difficulty is in the schlepping requisite
bottles of the stuff to camp.  A calculus must always be made between the weight
and the want.  To carry more than necessary is perverse, but to not carry enough
is torture.  Most thing exist between these two points of the campers continuum,
and one is always and forever reevaluating the point one thought ideal even
yesterday.

There is a process of purging, something done not all at once but slowly.  The
notions of ``need'' and ``want'' must germinate, must find a level not had at
first.  One has to come to the want first through need, which is not natural in
the plenitude of modernity.  It is a conscious diminution, a curling into
oneself to see what is left.  Having seen this play out another decade, the mere
act has become the substance itself, a weird inversion that perverts the


\finish

Before I ever knew of Trader Joe's as a shopper or an employer, I knew of their
dumpster.  It was a shoddy thing out back of a strip mall with the ally facing a
baseball field.  The route I had made for myself circling town, hit first the
dumpster at the Joe's, then Whole Foods, then a bagel shop.  By the time
of my retrogress, I would be laden with food, baguettes ties all over my
backpack because the center was full, and I biking full bore back home.

The dumpster at Trader Joe's was the most taxing of my foraging, jumping into
the Dumpster and throwing trash bags around.  It was no precise operation,
bags of pure trash from the demo to something filled with food from someone too
lazy to spoil the one bad jar in a case.  At this time the donations system was
not up and running well, and I would find myriad foods, enough to live on if I
had no other food source.  I was once more a primate gatherer, sorting the bags
of trash in a dumpster and finding the means to live.

Then it was on to Whole Foods, who would compress most of their trash in a
compactor, an act which will always consider disrespectful.  They left their
day-old bread out back in carts though, tied and sitting next to the building.
I never went without a loaf, the most rich and filling thing left in the back of
a store because it was a day not sold and now free.  

One was only to ever increase oneself both in mind and body, not
necessary in corpulence, but in ones adjuncts.  Accouterments all expanded
oneself, a form of the extended phenotype which would push the self outward.


It was over this summer I also picked up a job at Trader Joe's for the first
time, a place whose gravitational pull I would find inescapable for the next
decade.  Growing up in southern New Mexico, the cult of Joe had not yet made it
that far south.  The company still was primarily based on the coasts, not yet
moving inland more than in a odd city here or other. Santa Fe was one of these
odd little outposts, no other stores existing in any nearby states excepting
Arizona.  It was not for another decade that Texas  would get it's first
store with Colorado following two years after that.

\finish

And so I stocked frozen food and learned the lingo of the bourgeois foodie. I
learned that a boule and hummus made a good snack but if you had a bit of


The summer made campus no longer mine, the dorms closed and filled with
interlopers from other parts of the US, all twisted histories I never understood
landing them here.  My fellow classmates would all egress for the summer to tell
the tails of life outside the nucleus.  I would stay on, a summer job
keeping me instead in the sway of Santa Fe and in no desire to spend the time
south wondering what to do with my days.  Still I toiled with shovel and hoe
moving dirt and pruning bushes over the summer, now five days a week.  On the
weekends I would work for the on-campus catering, serving wine and food to
potential donors while trying to comport myself as a waiter.  All this came to
an end in a disagreement about costume.  I quite amicably and instead went
looking for work in town, ended at Trader Joe's, an affair that was to come in
and out of my life over and over.

\finish


Campus was still my anteroom, the gate to the trail on which I would ramble in
the dark of midnight after huffing my way up the hill.  There was a point in the
road where I could crawl through a tangle of bushes and reach the dirt running
track tucked off to the side.  From here I would follow the trail till I found
the gym set on the far corner, tucked down into a slope which would become an
arroyo passing in front of campus.  Here I would lock my bike on the rack set
out front, myself jumpy and moving fast in the light of the building.  The act
was natural after a week, a quick whip of the lock around rack and I was already
half way into the arroyo which lead under security, set up in their jeep and
guarding the bridge into campus.  There was some simplistic satisfaction each
time I walked under them and into campus, a little smile on my face as climbed
back onto the road right out of sight.  Now I had to move fast again though.  I
would dip across the lit street and into science building, always locked and
with no one ever around at the hour.  When I came down the hill in the morning,
this would be my first stop where inside there was a set of large bathrooms
complete with showers.  For whom these were build I never knew, but each day
would avail myself of the facilities fully to maintain respectability.

Night was a more of a sketchy situation, which required some innovation.
Creeping up the hill further, I would find the Uppers common room, a building
which housed a kitchen, couches, a TV, and other amenities not to be had in any
of the dorms.  This door was normally open all hours, excepting the summer and
holidays which would kick the kids out emptying the dorms for whatever repairs
were in need during the year.  Before making my move to Trader Joe's, I had
spent several weeks repainting the worst dorms, covering the walls with a sloppy
coat of eggshell for the influx of freshman already assigned this space still
dripping rivulets of whitewash to hide the year just past.

There is something inherently antiquated about the campus, as though the smell
of old books permeates even the dorms with walls the scent antiquity and
disconnection.  The internet would work only on occasion, most of the time
merely a false hope by which one would stare into the while page of a promised
connection that would never come, an exercise worthy of Beckett.  The
milieu was one of disconnection, an encouraged absence of the external and
instead to turn one's head to the back and follow a history of humanity
incorporeal and transcendent of the quotidian.  Why would one need the World
Wide Web, a suspicious alliteration of some superficial turn in understanding.

The buildings even evince an antiquity, and I would use this to my
advantage. Summer having come again to kick me out of my one school resource
still in need, the Upper commons room was now locked, and would be for the
several months to follow.  Yet being of an old construction, and given some few
scruples still unlearned at that age, I quickly discovered the door was easy to
jimmy with nothing other than my pocket knife, and in this way maintained access
to a sink for the remainder of the school break.  I had worked out the times
that security would come poke around the place, and would be in and out between
their rounds, or sometimes would just hunker down and wait while watching their
passing steps from the darkness inside.  

I have a distinct memory repeated the whole of winter break for campus, when all
leave to spend Christmas at home, a month hiatus of study and school life which
would leave me in the dead of winter without access to a place even to change
out of my biking shoes.  I remember many nights all blurred into a single
instance of sitting on the floor in front of the Coke machine, the red ambiance
just strong enough for me to sit and read a moment, to collect myself before
beginning the next leg of my journey, the hike up the hill through the snow and
cold to find my hammock so simple and evanescent in the light of the moon.

It was a weird sort of Bodhi tree to find myself beneath, those white letters
glaring out while I sat at its foot and considered the stream of events which
would lead me to this passing moment of illegal warmth and comfort before I
found myself again hiking into the dark woods in some strange dream, a raw
experience of something I could never quite understand.  History was always to
head in ways I could never quite follow, a series of events like philosophy
which would only ever argue with each other, the narrative more as conflict that
coherence.  I had plans of becoming an academic, to make philosophy a profession
and a muse which I could consult more deeply year over year.  Then all that was
gone, and now I had only a few strips of cloth hung on a tenebrous hill known
only to my feet.



\chapter{Hovel}
\label{cha:hovel}

\begin{poetry}
  Twixt dawn and days yet had\\
  Twixt a life still a dream proceeding\\
  And some yester year\\
  then only but proposition

  I move in lines unconvergent\\
  tilt a tide to wind my thought\\
  and flow...\\
  then in this unrepentant season

  In this space and no-place\\
  I make myself a myriad times\\
  form worlds by whim of word\\
  then destroy them

  I know now the Logos\\
  feel its cadence and its rhythm\\
  And move in time\\
  then quick and without worry

  This dance, YAWAH's dance\\
  who knows not himself\\
  but by an alchemy\\
  then but reflection in his creation

  Yet morning breaks on some sharp shaft\\
  of light, of necessity, and becoming\\
  I collect my dreams from twisted sheets\\
  turn each and query a clue\\
  then to Night return them
\end{poetry}


History is something I came to late, having ignored most of it throughout my
high school years as something unnecessary, and through college as an excess to
be always indulged in later.  Philosophy would ever ask us to devalue the date
from which each new system emerges, and instead believe it to speak only of
eternalities outside of time.  This is all pretense of course, the age baked
into each as irremovable as the language used to utter this new dispensation.
Unfortunately, one can only come to this conclusion first by knowing enough of
an age to understand how it becomes *episteme* all and assumed without
question.

History is a tricky beast, in no way serviceable except as a means of
understanding.  A myriad and banal platitudes have been written on its behalf as
it is indeed in need of some explaining.  These range from the threat of
repetition, like time is cyclical and only with our wits can we escape its
gravity, to the \textgreek{ἐντελέχεια} being something discernible if one just squints
though some lens like the materialism of Marx or the systems of Spengler. Some
would have us place our purpose back in the dead hands of the past, querying our
ancestors for what we are about in this age.  All these are interesting at best,
as is the Ptolemaic systems of the stars in its ability to convince one of
untruths.

Each epoch springs anew, pulling us into permutations unthought of before we all
just found ourselves here.  Modernity is a vast acceleration upon the whole
machine, the zeitgeist zipping along at such a clip it even abandons its own
children along the way, whole generations left stranded and wondering where
their world got off to.  History nowadays rarely even rhymes.
\finish{}

The job was unclear but the pay was good.  I was to move mail up and down a
mountain, the mailman for the post-office.  I was to be a ``subcontractor'', which
at the age of twenty-one sounds as though one is doing something important, that
some trust has been given.  I gave up the life in Santa Fe,  packed everything
into the duff bag and rode south on the bus, the long track down the state.  Now
it was time for something completely new.

In two cities I would live, one in the mountains and one in the sand.  A truck
was to be mine, driven back and forth over eighty miles each day split in
halves, the day in Mayhill, the night in Alamogordo seven days a week.  My life
was to be bifurcated, one in a town so small that Main Street ended at 12, and
one in a town I kept at arms length.

Alamogordo, population 35,000, was a place no one thinks about living.  It is a
place to be born or a place to die, but both only unwillingly.  I would never
come to be a part of this town, always living on the edge of something here,
physically and mentally.  There was some disconnect to the place I cultivated,
in its way enchanting, unsure.  To be here was to be nowhere, to not belong to
the place I was.  I remember the de-centering, the feeling that I was both at
home and not any place in town.

The Sacramento mountains flank Alamogordo forming a backdrop to the west of
town.  The mountains rise first roundly, then starkly five thousand feet above
the city.  To the east, only the horizon hundreds of miles away forms the rim of
a flat desert without differentiation.  In 1945 the US government built a
sprawling military installation and missile range in vastness of the desert
outside the largest gypsum deposit on earth, White Sands Monument.  Not long
after, the first atomic bomb darkened the skies above this barren basin.  After
the war, V2 rockets were stolen and refined here.  What missiles now ply the
skies when the highway closes during test flights I leave to the imagination.

When the wind would kick up the sky to the west would turn white, gypsum clouds
thrown up from the dunes and hovering in the sky.  The dust was everywhere, a
powdery dirt that would coat everything.  Biking through this particulate wind I
would have to squint my eyes till nearly closed, they still caked with sand, red
and tearing by the time I arrived.  

I bought an old 10-speed Reighley racing frame while poking around a bike shop
and had it stripped and remade into a beautiful ride.  A Selle Anatomica saddle,
new cables, tires, spokes, chain, and grip tape.  After replacing the peddles
with toe clips I could hum around town with no special accouterments, still
sleek and fast. Tube-shifters makes the riding experience special, something
akin the driving a standard transmission.  The act of changing gears becomes
costly, it cannot be done with abandon like with brifters.  To pedal then is not
to run that one easy crank RPM too natural, but to feel the range, the hard and
easy, to start with strain and end puffing.

And puff I did, the city sprawling in a way that only America manages, roads
drifting off in all directions lined with shops and nothing in between, islands
of industry in a sea of sand.  I would bike Walmart on the northern edge of
town, and buy my dinner, some days soup, a baguette, or chips and salsa.  I
could eat for under three dollars most days, banking most of my money for the
future.  Eating food in the front of the store became a ritual, spooning some
cold food into my mouth from the jagged top of a tin can while watching all the
families living their lives, in and out and shopping and home.  I never desired
to be any of them, to live a live set-piece, something fixed and prescribed.  I
would rather be homeless, be free of something I was scared of, something I
could not name but would fight intensely to avoid.  Walking the middle class
neighborhoods at night, glancing in windows where every house had a TV blaring
and a whiff of stagnation, of the quiet life of desperation.  

Nights were spent on the south edge of town, locking my bike last light post
before I hit the darkness of desert and open land.  I crossed the street and
climbed a hill inaugurating the Sacramentos, higher and higher till I could see
dark city as a mirror to the stars above.  It was only in the night I could
climb and not be seen, the desert too naked to know any modesty about who beds
in her bosom.  Desert inclines are always steps, swathes of elevation which
suddenly level as though the hill were unsure of itself, before continuing again
its incline.  The first mesa was my choice, a struggle against bushes and cactus
till I topped the side and would check for cactus needles caught unbeknownst to
me somewhere.  In the summer I'd strip to my skivies, hang my sweat-laden
clothes in a bush, and unroll my tarp.  I made a game of toughening myself to
the ground, to the rocks and the debris beneath me, each night choosing ground
slightly less even, less inviting.  One night the rain had come cold,
unexpected, and sideways with the wind.  I rolled myself into a burrito, blue
tarp holding off the cold rain seeping into the old fabric, the old holes.
Lying on rocks in the desert, wrapped in an old found tarp while shivering
uncontrollably, all I could think was, ``Well, this will be a great memory!'',
and dissolve the present in the future.  Everyone has their own quantification
of ``tough'', and I chose mine abstrusely.

4:00 AM the alarm would sound, a battery-powered travel clock dinging away into
the open desert at the corner of the tarp.  Everything was rolled and strapped
to my backpack in the dark, then I would be off ambling down the hill to my
bike, always worried it wouldn't be there.  Once alight, the rest was easy,
flying down hill to my truck parked safely in town, to load up and start the
adventure up the hill again.

When the truck rolled up to the loading dock, there would already be waiting a
fleet of metal cages on wheels set to be rolled up the ramp and into the truck.
Everything was ratchet strapped to the walls and then off up the mountain, five
stops in all to dump a cage or two into the back of a glorified shed known to a
town of population 100 as ``The Post Office''.  The postmaster wouldn't be by
till 8:00 AM when I would already be slipping into some dream again as the sun
was just really coming into it's own.

The truck emptied, my journey would leave me in Mayhill, a town overly gloried
by merely having a name.  It was more a slightly denser collection of houses
strung along the valley, most still trees and fields.  The only commercial
activity in town was a gas station, a feed store, and a barber.  On occasion a
restaurant would pop up for a few months in the empty building next to the feed
store before predictably going belly up soon after, a rotation of owner and
entrepreneurs who would not take no for an answer.  The place would be spruced
and cleaned, redone, and opened again.  The same handful of old cowboys, men
grudgingly retired but still wearing their spurs and wedded to a work they no
longer had, would amble back in like nothing had changed.  To venture inside was
to know one's self and outsider, not part of the morning huddle to talk over the
valley news, a horse dead, a buck seen, the way the world was on some tear
taking everything into cities and lives far away and never to be understood.
Show a man like this his house on Google Maps, a satellite view of his truck in
the driveway, and he will be on immediately about the second coming being near.

Past the quondam and future restaurant, a snaking dirt road led up an
undistinguished hill, rising up past the gas station and onto a flat bit of
grassy terrain, in the middle of which was something generously called a
``house''. What sat there rising above the overgrown grass was more a hovel, a
half-build shed over a twisted travel trailer.  The axles had been taken off the
trail and the whole thing set on the ground to rot away at a rate unequal to its
additions.  A gabled roof was set above expanding the footprint by half, with
walls coming out to enclose another room build onto the side.  The addition had
been framed and insulated, and then given up.  The insulation hung limply from
the unfinished walls, slowly shedding their pink innards to the air and onto any
clothes or a limb passed too close.

There were no shingles laid skyward on the roof, only graying plywood warped
and fraying at every edge.  The ridge-line was open to all elements, and When
the rain came, it would come in torrents down inside the walls, channel unseen
in everything, dripping out sockets and window frames.  A bevy of ice chests
\textit{sans} lids were ready at hand, hurriedly thrown in position as to
collect the emerging streams sprung inside the house.  Above the bed, water
would work its way between the paint and sheet rock, forcing down till it had
bulged the paint into a perfect breast hanging solitary from the ceiling,
lactating from its most prominent point down onto the bedding.  One ice chest
was for the bed, centered and left overnight in case the weather changed after
the mail and I migrated down the mountain.  The one time I left forgetting, the
bed was soaked through the next day and onto several expensive books I had left
lying on the sheets.  There was no safe place for books, each time the weather
came some new stream would appear in a place never wet before.  To this day many
of my water-warped volumes are from this time. 

The bathroom was a toilet and a old tub set right on the dirt.  The toilet was
the singular element hooked into a sewer system, the bath tub just piped out of
the hill a little ways down.  A wall had been framed up and put around the whole
affair, but these new walls didn't match up with the main gable, so with a
little corrugated metal and a few more 2x2s, something resembling a roof was
thrown up, never mind the large gaps.  The bathroom was well vented, especially
when there was a breeze.  For the floor, a refashioned piece of blue carpet
whose appearance was of second-hand at best, was cut to fit and laid down on a
smoothed dirt, still in places lumpy.  The wet ground beneath would wick into
the carpeting so that walking would make a squishing sound.  The day after a
fresh rain, I would arrive in the still breaking dawn, and there would be big
beautiful mushrooms sprung up overnight, arrayed around the base of the toilet
and growing right out of that blue carpet.

When the season had turned and winter came round I found a different set of
problems.  The bathroom was too porous to the outside to be heated, the walls
having no insulation and the gaps in the top distinguish it little from being
outside. The sole heat source was an old oil heater run off a butane tank
sitting outside. The thing would crepitate and hiss, but for all it's pretense
could only really change the temperature of that one small room while still
burning an insatiable amount of propane.  Now instead of collecting my morning
harvest of toilet mushrooms, I would flick matches till I got the pilot light
going on the heater, and then grab a trowel I had sequestered as a ersatz ice
pick and head into the bathroom.  The task at hand would be to chip enough ice
out of the toilet to allow it to function properly.  Sometimes this would just
mean stabbing at the ice in the bowl till a flush would not overflow after
filling the small remnant above the ice wall. Other times the job would require
several liters of hot water poured from the tea pot into all parts of the
toilet, and then flushing and hoping for the best.  I learned to control my
coffee consumption till I was sure everything was working properly, as my
plumbing was always fine after the second cup. 

In the winter I moved to the truck, the desert too cold for my gear.  It was
something like an unpainted U-Haul with a little door between the cabin and the
box on the back.  If the door was left open, I could sleep in the box with my
head not far from the door.  A second alarm was bought, this one set a ten
minute interval from the first.  Now when the first alarm would sound, I could
stretch an unwilling arm out into the cold enough crank the key set ready in the
ignition.  Retreating back to my sleeping bag, I would await the second alarm in
my half-dreams till the cabin was hot with the heater blowing full blast, the
engine now warm.  After a clamber into the cabin, always ungraceful at this
hour, the Thermos of tea made the evening before was perfect temperature.  Hot
tea in the cold of morning will always convince me that my life choices have not
all been bad.  That first drink still in the haze of dream. 
Pulling my bedding behind me into the passenger seat, I'd throw the truck in
drive and zoom off to get the mail one more time. 

Storms would cover the highway, a tenuous road in good weather and always
subject to rock slides.  The sheered faces were netted so boulders couldn't
launching themselves too far, yet this could never prevent their eventual
landing in the middle of the road.  It was no rare event to discover the road
nearly blocked by some few tons of stone just around a bend, now taking the
majority of both lanes.  The highway department would be out by the time I was
retracing my tracks, guiding traffic around and attempting to undo the damage.
Once up the hill, the road leveled off and turned into a snaking valley.  The
stream and cow pastures would entice all the wildlife in those dim hours while
the dew could still be seen hovering above the field full of deer.  The elk were
most normalized to the road, grazing just off its side, watching with
indifferent eyes as my truck flew past a few feet away.

\starbreak

In Mayhill, the last address on Main street belonged to Gruncle Brew, my
grandfather's cousin whose connection to the family become something fuzzy enough
for a neologism.  Gruncle Brew, the old cowboy, born in the dust bowl and pushed
west with the rest of his clan.  He landed in California like most did,
scratching his way as a young man till he was no longer.  I only know him in his
second act, retired welder, grader, cowboy, handyman, moonshiner, and chicken
fighter.  He had stories of wrestling cattle and welding up a moonshine stile in
Louisiana somewhere out in the bayou.  He had once build his own dump truck and
hired himself out moving dirt.  He was one of those people who was too poor to
go to school but too poor not to know how to do everything.

He still had his game cocks locked in pens in the back yard.  The hens
were worth more, breeding stock like money in the bank in Mexico.  Yet no one
came to buy a bird so far away and up a hill in the middle of
nowhere. Cockfighting was banned in every state now, had to go all the way down
to Mexico.  Brew would always be on about going down there, to go make some
money, but he never would.  He would raise his chicks and sell to no one, each
generation instead growing the number of cages.  In his old age he become
attached to his birds, too much time spent there with them, sitting out under
his elm tree.  Each morning he would prepare their food meticulously, passing by
each cage in turn, his little wiener dog named Princess always right behind. He
would ladling just the right amount for each bird with some formula he'll take
to the grave.  He couldn't fight them, yet couldn't give them up.

I learned to play music from Brew; or, rather, I learned to want to play music.
He had an old Martin with the frets worn down to the wood he would pull out and
suddenly the gruff voice would change and he was mellifluous.  All the
intonations of a hard life were gone, and instead he would croon some sweet
melody over that old guitar whose wood was old as he was, older.  His daddy had
bought his that guitar when they still had dirt floors in old Cali.

It was not the glories that he would remember though, it was only the faults.
Night were spent awake, thinking of the past, of all the moments gone wrong, of
all the things which should have been, been said and weren't, all the things
done now shameful.  It was the remnant of a life as most was even now the past,
his faith in heaven the only salvation.  He would endlessly talk of the bible,
of things yet to come, of times of perfection unable to be had in days such as
this, in the fallen world, a Kali Yuga of the age and himself.  The ceiling
above his bed was his tormentor, staring like the void back at him in the dark,
convicting, convicting.

He came to Jesus hat in hand, came for forgiveness of a life gone somehow all
wrong, the next life there to try again, to get in all right this time.  Somehow
things where always askew, how?, never sure.
\finish

I would come wandering over and we would sit out back drinking beer, he filling
me in on the chickens, and I would tell him about what I was reading or learning
on the guitar.  It was about this time that the conversation would always
descend, spiraling into religion.  Bible references would flow off his tongue
like Monty Python quotes from my sister, everything a fit subject for them and
always thought apropos.  It is interesting to observe the mind of someone with a
reference so different, a starting point a world away like the sixth Euclidean
axiom somehow missed in class.

He had systems worked out, nights spent in the book of Revelation charting
genealogies and creating tables.  He had mapped the second coming, the Parousia.
He was sure the days of retribution were nigh, coming like a thief in the night
and it was for the living to watch for the signs and symbols, news he would
gather from his dissident cable box, piecing things together from Christian
TV programs discoursing on current events, to Russia Today and Al Jazeera.  He
had bought some cable box year ago that gave him access to all free Christian
and news stations, and he had made a patchwork of their content, half the time
arguing with them, there alone in his living room, the other half the time
importing some new story he had just learned.  We would go though his stations
sometimes in the morning, he telling me about the news the day before and its
implications to eternity and always so sure that this was the last days.

In the end, there was some asymptotic point we would approach from both
directions, I arguing one side and he the other. ``Look around! Obviously there
is a God!'', he would at some point finally declare after hours of circling the
subject, arguing church fathers and biblical sources.  I could only ever
respond, ``Look around! There is obviously nothing controlling all this!'' And
there argument would have to rest, for in the end, there is only the sense of
things, irrational and unmovable.

There are too many points in philosophy where one ends in a cul-de-sac, a point
at which there is no escape.  One can come to this from both directions, from
the experiential then to the logical, or the other way around.  Topics like free
will vs determinism and deity vs chance are such paths that end nowhere, alone
and irrefutable in a way that is no longer explanatory.  At these points, the
only thing left to do is retreat to something more general and start again, to
know there are a million rabbit trails that leads to nothing, to contradictions
inextricable like Godel show the Logical Positivists.  Philosophy is a blunt
instrument, and its applicability is limited to a scope smaller than it would
seem. 

The conversation having flagged, we would go to the kitchen to eat.  In his
refrigerator sat an eternal stew, a big pot with stains on the side, taken out
from its prominent place and placed on the stove to heat.  He would dip his bowl
each day, then rummage till he found some errant veggies or meat remaining in
the fridge, and chopping them imprecisely with his pocket knife throwing them in
the pot.  It was an evolutionary process, each day modified by the additions of
the day before, each day slowly becoming something new.  We ate that same stew
for the year I was there and I never ate the same stew twice.

\starbreak

The mail job had become an inextricable part of my life after a few months.  One
can never escape a job which is seven days a week, morning and evening.  When
the weekend comes normally, there is a certain irrationality to the two days
where everyone convinces themselves that a huge span of time separates the
present from work, an epoch all condensed into the next two rotations of the
earth.  Given only at most a 12 hour window till the next round, life becomes a
pattern continuous, a much smaller cycle with no breaks bound by a seven day
delimiter.

This was a time of the blurring of bounds, both spacial and in the separation of
time and work.  I would create a cycle for myself, each day here, then there,
then work, then bike, then a new place.  With the unfixed arrangement I had for
a home, this cut the cord attaching home to a defined location.  With a job that
I was always inevitably on my way to, there was never such a defined time
between week and weekend, and between work and home.  It was an odd
homogenization of existence that I enjoyed and hated in a way inextricable. 

In this job I learned to fear time.  The much to used adage that the mail must
always go through was true to my station. Three times late in two years and the
contract could go up for big again, and bye bye my job, and maybe the contract
owner, Jed.  The last driver had run through two of those leaving me none.  It
was for me to be there everyday, rain or shine, sleet of hail.  Jed have sold me
the truck, packed his things from the hovel, and moved to Iowa where he bought a
trailer and setup a new life.  I ran the mail and we both got paid, the Walmart
travel alarm the barrier between both our jobs and filing for unemployment.

My paranoia started with the naps.  After a 5:00 am shift, I would come rolling
into Mayhill and crawl into the bed housed in the hovel, not yet ready to
approach the day.  The sun would just be up over the mountains and I would be
once again in some dream of people past and time outside time.  I would crack a
lid, that tiny shaft of lift into my retina, and with a logic incoherent I would
come flying out of bed, sure I had missed that hateful alarm and the day had
come without me, I still supine and the mail waiting on the dock now for someone
else to come collect it.  Having hove myself into the middle of the room, head
not right but my pulse already up, I would stand dazed, and wonder why I was
already in Mayhill, what this meant and why I had stayed the night here.  Then
the morning would come crowding back like the end of a mushroom trip, the
contours of life reshaping themselves into some linear timeline.  I would begin
to play back the day so far, and at some point discover that the job was already
done, that I was indeed in good stead in life and all was okay under earth and
heaven.

Soon these panicked moments of hypnagogia would grow into my nights, inserting
themselves as dreams that the alarm was going off.  These would immediately
awaken me in some grumpy state, only to discover that it was not yet morning
time, but still merely a sliver into the next day and still deep into the
predawn.  Angrily I would resettle myself and drift back off and into another
dream to await the real alarm which always sounded too soon.

My paranoia found an even more invasive evolution though, such that the dreamed
alarm would not only sound, but included in it's fog was now my checking the
time.  Being that infernal beeping was already haunting my dreams, it did not
take much to then include within it my wary response, which was to grab the
clock and see where things truly stood.  One my subconscious realized it could
integrate this act into its fictions, there was to be an expanding suspicion
about the true time of night.  I would dream that an alarm was sound, so I would
dutifully grab the clock and half asleep still see where things stood.  If still
in the early hours, I would toss the alarm away and being the downward slope to
sleep again.  But then the question would come creeping in --- Did I indeed just
check the time, or did I dream I did and merely turn off the alarm?  I had
indeed done this once, but came back into reality in the moments after while
still holding the clock clutched to my chest while I was about to drift into
oblivion again.  Now I never knew the truth, or was forever unsure of my
knowing.

Thus began nights confused with reality, always lying there on some edge of
reality but forever unsure of its bounds.  I would dream myself checking the
time, of setting alarms, of unsetting them, and of my panic when the fog of
dream had cleared.  The cycle would progress as a series of questions followed
by actions also immediately in doubt:  Is that the real alarm? --- Let me
check. Oh, that was just a dream.  Wait --- did I really just check the time?
Let me check.  Ok, its still early. --- Wait, was that a dream?  Let me check
---

I had once been lying there for an exhaustive spell arguing as to whether I had
indeed been awake, when finally convinced, I got up and dressed, packed my bags
and was ready to head down the hill when I looked to see that all had been a
dream, and I was a good four hours early.  It is an experience which I would
liken to those with dementia and know themselves only later to at times slip out
of the common spaces.

\starbreak

Days I didn't go in search of Brew, didn't find him sitting in his
camp chair out back by the tree, I would bike.  My tour bike was set at the
ready, always oiled and aired, cleaned and calibrated.  This place was a way to
the future, to leave this hovel to rot into the ground and cycle off in some
direction for no reason at all.  I wanted most to have no map, no timetable, and
place to call home.  I wanted to improvise each day, to choose who I was each
time I rolled into town for a day, an hour, or long enough just to peddle
through.  I wanted to exist only in the short-term memory of everyone I met, a
passing face to recall never again.  Wasn't this real freedom?  How could
anything else be, bound by everyone's idealization of yourself, a mental model
existing in someone's skull of you.

So I would push off from the hovel drive and onto the highways which spidered
the mountains and valleys of New Mexico, long winding roads with no one but me
there.  It would be hours sometimes before some care would crest the hill ahead,
a dot still, and grow till it finally passed, only to change octave and recede
till unseen around a bend.  Mostly the roads where mine, constructed for me to
find a lonely happiness out there peddling with all I had.

I would each day push to find that place of remove, the place after the
endorphins fade, after the burn of muscle dims, after everything had been given,
and there was nothing left but that crank turning, turning, turning.  It was the
meditation of action, the silencing of mind my having no energy to think of the
past or the future, it was to be empty.  It was to find nirvana, not that
heavenly bliss nonsense, but the snuffing out, the nothingness of the I.  

Then one day I pushed too hard, too fast, too far.  I climbed to Sunspot, an
observatory forty miles of mountains and valleys three thousand feet above me.
I rode so well that day, there and back in five and a half hours. It was also
that day I partially ruptured my quadriceps tendon in my left knee and killed
all the plans I had made for myself.


\chapter{Arroyo}
\label{cha:arroyo}

\begin{poetry}
  I walked amain in a thicker time\\
  with a spoilt sun which licked my hide\\
  It wheezed to me of things unclean\\
  till I was sticky in corporeality

  What farse to tug on strings from higher things\\
  a wash!\\
  I need to wash!\\
  my humanity.\\
  Romance dies to a carnal thrust\\
  of dirt\\or sweat\\of heat\\and dust.\\
\end{poetry}


I still remember that day, that glorious morning with the sun just set perfect
in the cool mountain air, and I on my shining Katje riding down the gravel road
till I hit the asphalt of the highway.  I felt powerful, my legs filled with the
adrenaline of what was to come next, the miles and the constant spin of that
crank that would subsume the complexities of living and leave only that one
task.  I started slow, knowing finally how to pace myself, or so I thought, how
to measure out my resolution over hours and miles.

I rode first the the city down the road twenty miles away, speeding along like I
normally did on this stretch with the incline not to steep.  After stopping for
an energy drink, I took the road south deeper into the mountains and all
acclivity from here on out growing until I had traversed twenty more mile and
topped out at the solar observatory so aptly named Sunspot.  Now for the
regress, flying down at speeds faster than the traffic of a few solitary cars I
overtook waving as I went.  Downhill was never a time to rest, but merely the
moment to test my gear ratios and push the lowest rings I could, still giving
everything I had to fight the wind for that asymptotic 50 mph I never managed to
break.  Somewhere in the stretch along the peaceful stream rimming the valley
pastures with slight slopes rising and falling, something in my left leg went
wrong.  There was a sudden slackness in the joint, as though things could move
too freely.

I would later come to learn I had partially ruptured my quadriceps tendon at the
point it attaches to the patella, a point that necessarily must be taught to
support the correct movement in the joint.  It was an injury of nothing more
than pure exertion pushed too far.  I would come to despise the trope so
frequent that one must only push oneself to succeed, as this can work just as
well in the opposite direction.

That morning, I had left felting I could traverse the globe given enough time,
my body hitting that sweet speed of revolutions so many hours ingrained into my
thighs that would carry me indefinitely into the horizon.  It would be the
metric which I would judged myself ever after, the moment of my ultimate health
and vigor, and the moment of my decline like an inflection point more definite
than most in life.

One forever wonders what would have come to be if one choice were made
differently, a choice which diverts the course of all thing which follow after.
These are all counterfactual musings which cannot be known, only fictions
concocted about what would follow had the story had a different twist.

Most of life is plan that fades faster than can be written, the ink
disappearing behind the hurried scrawl of schemes and aspirations one is ever
acting out.  The wheel of karma turns to a tune which we will never know and
cannot fathom leaving us to endless rewrite the script of our individuation.

My knee, the eternal failure in all my aspirations was to be the bane of every
plan I had concocted for the next several years to come.  I had worked so
diligently to cut all connective cords to most things in life, to simplify to a
mere bare bones so that I could come and go from people and places as I wished.
I had discovered a Christopher McCandless' somewhere inside myself before I knew
his name and his story, and had centered my self as approaching more and more
this ideal.  

Then I had destroyed my good health, a fall from the heights of good health and
resolve to a state lower than I had ever found prior.  I had quit my job, and
only had a hobble to show for it.  It was all Will until it was biology, and
then a reevaluation had to come.

And so I moved back home, staying for a tide with family, my grandmother for a
moment, and then my mother's house where I took up residence in a nook under the
attached island splitting the living room and kitchen on a bit of floor which I
would unroll my sleeping bag each night.  Appointments with doctors and physical
therapy would follow in abundance, a cycling series which I shuttled between,
all my savings ever on the decline.

This was a stable pattern at least for a while. There was still something
stultifying in the whole situation, I in an seemly eternal holding pattern while
I awaited my health to return.  I would spend my days in study, some attempt to
salvage the present stasis by attaining some intellectual feats.  My lack of
owning a vehicle, and given the remove my mother's house sat from town, there
was nothing much  other than the desert in walking distance and no one which I
knew or cared to.

It was not until I started writing down my life that I have come no realize how
few friends I have kept at most points, generally their number approximating
zero.  Part of this was the situation in which I would find myself, and part was
just a disposition.  I find an integration problem most times, all my interests
being solitary and seldom shared, myself toiling away at some talk given as
penance or distraction, I never sure which.  And so I studied tirelessly in some
attempt at integration, an indistinct notion that all ideas pointed toward some
premise which could encapsulate them all. 

Once again I lived on a divided plane, civilization on one side and the desert
on the other.  It was a space that I came to inhabit naturally, never really
giving in to modernity, yet never the Luddite fully either with the next decade
seemly waffling between the two poles closer to both than anyone I knew.  

The days were long.  I had undone half myself, now only the mere mental
remaining.  I could only hobble and so decided to instead invest in my mind.  I
would follow the interests as they took me, and see to what end all the study
would tent.  Languages and logic, novels and history all crowded my days and I
tore through stacks of books and literature in some vague attempt at a
clarification.

My interests have always outpaced a point, and instead I found myself merely
staggering this way and that in search of a connective thread to which all these
threads were to tend.

\chapter{Cabin}
\label{cha:cabin}


\begin{poetry}
  Remembered mornings come on occasion to remind me\\
  It was the silence\\
  the queer day still unsure as it came mute to make jagged
  once more the dark horizon\\
  I sat still on my porch\\
  to watch
  
  In the air the smell of wood\\
  the fragrant fibers in newly placed walls\\
  feeling what they should contain\\
  Of ash, smoldering a small heat\\
  while I shiver instead and stare\\
  at the act of a day becoming

  I try to recall the emotion\\
  the long forest between me and the world\\
  out there inchoat in idea\\
  It was a simple contentment I had made\\
  a renewed childhood!\\
  To be hungry was to eat\\
  to be sleepy was to sleep\\
  to be awake was to play in a cyclical stasis\\
  My world was still
  
  I would ramble through the forest\\
  to see as much of the century as I could\\
  the sun's dusty heat in tow to erase my steps\\
  Or was I also part of time here\\
  a piece of cycle\\
  that man should walk lonely\\
  through the hills in search of something?
\end{poetry}


The cabin was half-built.  Two rooms set on the side of a hill connected barely
by a rugged hole cut between them in between two studs set 16'' apart.  Raw
plywood covered the whole place, painted hastily in a single coat of now peeling
white.  Inside, studs stood like ribs with open insulation still slowly
compressing down inside the walls.  Mouse droppings littered the floor in the
corners and a million dead moths lay still on the windowsill in an array
worthy of divination.

No one had lived here for the last year, my aunt having moved into a valley on
the other side of the mountains with her new husband.  The construction here had
come to a halt and left to be reclaimed by bits of the forest as they worked
their way inside day by day.  

Outside a sea of small scrub oak poked out from the rocks and the pines.  This
far up the hill, the trees were all small, fighting for life with more stone
than soil.  Even the single road which approached the cabin was paved with sharp
stones which required one drive carefully, slowly and hope to still have a full
tire the following day. This was but the last bit of a road seven miles long
which lead through the national forest before one came to a turn off which lead
up this one stony hill leading us all to the sobriquet ``Rocky Top''.

Rocky Top was to be my home for the next year, a solitary moment in my life
where I had no one else to commune with except the silence of the forest.  Still
broken with a bad leg that would allow me to work only intermittently, I could
pick at the place, slowly remaking my little world on the hill.  This was to be
an experiment in deprivation, the limit of aloneness that I could indulge.  It
was to see if I really was autonomous in the ways I would proclaim myself in the
dreams of some far off self which had separated from the world.  I had no
vehicle, no escape once here back to the world.  I would rely completely on the
periodic deposits of food and supplies which my aunt and uncle-in-law would
bring around every other week or so.  The rest of the time  was just that
pervasive silence which builds to a crescendo that hurts the ears.

It was in Aristotle's book on politics that is states it is only for beasts or
Gods to be alone, the rest of us must live in some communion with others if we
are not to go insane.  I have remembered this dictum through the many years and
still sit in contemplation of it at times.  It is only in this day that we worry
we are too mechanized, an automaton which acts not as an individual, but instead
a mere cog in the machine which is modernity.  For the Greeks, those to fear
were too near the beasts, antinomian in their acts and governed by mere emotion.
The struggle of Man was the fight against this side of himself till he had
pulled his being back in line with a logic of the heavens, perfect rotations of
reason and morality.

Yet it is the beast which is also alone, for \textgreek{ἀρετή} can exist only in
relation.  To escape to the forest is at once to be less than virtuous, instead
having occluded even its possibility.  One then becomes outside the world of
Good and Evil, instead just a discreet existence with no relevance.

It is not unlike the end to which Nirvana is set, an evolution to the Hindu
karmatic cycle by inventing a method of escape.  Hinduism was the attempt at an
affirmation worthy of Nietzsche who would have us imagine a world where we were
all caught in an eternal recurrence: Given an universe swirling around in an
infinite number of permutations over an infinite period of time, our lives must
be relived an infinitude of times just by sheer chance.  He would have us use
this as a test to one's ability to affirm life in the face of this.  Who is it
amongst us who can say yes to reliving one's experiences a unbound number of
times all without an evolution, nothing gained or lost and only repetition?

How could the Hindus not have reached this same conclusion, their permutations
the product not of the formulas astrophysicists invent, but instead all the
spinning of the eternal karmatic wheel, which leads each up and down in a
predictable pattern not less than that of a pure mathematics.  One's good deeds
will move ever upward in the evolutionary ascent of the soul till one has become
a god.  But always at this point, it is the arrogance of such a station, the
power and acclaim that will in the end pervert one's acts to such a degree that
like gravity, the soul must come crashing down into that of an insect crawling
along the ground.  Cycles move within cycles, yugas turn and we all are stuck in
not the same lives but forever in an ignorance which will come in waves.

Thus the Buddha came to proclaim and end to the cycle.  He would have our end
Nirvana, the Sanskrit word to snuff out like a candle, to extinguish the flame
of ourselves permanently and instead scatter into an existence so diffuse as to
undo the I.  It was to finally end a life and have karma without remainder, the
settling of all debts cosmic and otherwise such that one is no longer entwined
in substantiation and can pass into an un-being.

All those who pursue this attempt at ultimate separation are in essence trying
the same trick the Buddha did, to unmake a karma and instead exist in a way that
requires no connection.  If we are to believe David Graeber, there is no
primitive land where barter held sway and all must have a double-coincidence of
wants.  Instead all societies first found a means by which to maintain an
inchoate balance with all others, an ethereal system of credits and debts which
would situate one in a community.  To have a net balance of zero was to be a
foreigner and to have no history.

Even now we come to history as a series of cause and effects, a moral frame that
requires action as though there is a necessity that all ethics finds the origin
point and canceling to nil.  We assign each history of a place or a people the
same karmatic soul as though there is some current account which can be
calculated and held against another nation.  All history is an assumption that
the mass of men can be praised or condemned as though we are all still Israel, a
people with no plural and deserving of punishment \textit{en masse}.

\finish

The dream of divorce from the web of interconnections was a dream long held by
myself.  I had wanted to move through life only in the short term memory of all
who I passed.  I wanted to float free of expectation which seemed to me an
unacknowledged debt placed from one upon another even without contract.  It is
to be called to a self foreign at first, and be required instead to identify
this as one's own like a bizarre bifurcation of reality.

I would be free of history, the necessity of self constructions unneeded and
could instead truly live in the present uninhibited by my self.  History is
always a tyranny in the end, a place to house all the ills of life like Freud's
Unconscious.  One tucks into the years so much to regret and to wish were not
so.  It is only by constant action that most unfind themselves, or with the help
of some foreign mindset found in a molecule alimental to brain chemistry.

Yet here I sit building some edifice of memories.  But these are all placed
perfectly in a world clean of discord and dissent, a tale one need not question
for it is no exemplum.  I write for the future, for those who want to dip a toe
into the life of an ancestor and put flesh on a name previously bare.  This is
my attempt at self-preservation, an extension over a few generations more before
all these words will fall into the dust of time and I will accomplish my old
goal at last of a name that all forget.

Here it was that I would bide my time, stew in the mornings, writing poems to the
day.

\chapter{Ridgeline}
\label{cha:ridgeline}

\begin{poetry}
  I wish to you a word to tip the world\\
  A song hard and sweet as dirge to sorrow\\
  A viary chant to chance a hope I cry\\
  To you of the long tomorrow.

  And so I go with penumbral sounds\\
  A verse to terse, to kthonic to find sublimity\\
  They but glissade and skate and scatter\\
  Upon a world whose word is still\\
  sorrow.
\end{poetry}


Santa Fe has some mystic call in the old architecture still stained with the
centuries, it betrays its age in the wrinkles of twisting roads, of a place
preserved and out of time.  In 1598 Juan de Oñate and his *Conquistadores* has
reach the limit of their greed and gave up on El Dorado, instead setting up an
outpost at Ohkay Owingeh where he would call the place Santa Fe de Nuevo
Mexico, a new province for Spain and for the glory of the Empire.  Later the
capital was moved to a new city at the feet of the Sangre de Cristo mountains
called *La Villa Real de la Santa Fe de San Francisco de Asís*.

The city still smells of Conquistadors and Acoma, of the fervent faith of
Catholic priests set in a desert land, sent by their god to contend with those
who lived pastoral lives in an age lost even then to time.  The Pueblos, brown
houses of mud build to house mystics all, closed in the earth except by a hole
pointing to the sky.

The pull to Santa Fe is that of gravity for the broken.  The earth here calls
across the continent to all those who must begin again, to remake life this
second time.  They come here not knowing why, but come they do and end here in
adobe walls waiting, the kiva still unlit, for some spark to turn the tide of
life.  For some it does, the spirits in the air right for some transfiguration.

I came again to Santa Fe to rebuild myself, to rebuild the body both in flesh
and mind.  I had come to consider myself first a broken thing, an incomplete
life that was filled first with problems, second with aspirations.  I had lost
the sense of self-actualizing, that pure will could indeed move the world if I
could just concentrate it in sharp enough a point.

My mom and I drove the barren back roads up to Santa Fe with a truck of camping
gear and a bag of clothes.  I had bought a plastic bin which was to house a
handfull of books in the uncertainties of the forest.  I had come back to try a
second time, to make my start this time further up the mountain, this time on a
ridge that brought the whole city into view, a set of blurry colors so
indiscreet as to give me proper perspective.  It was the view from Olympus, all
below washed into broad strokes of a landscape larger than could be seen from a
point of differentiation.  

The desert was too much, living in my tent at the edge of down, eating Ramen
noodles cooked over a camp stove swiveled onto a canister and set in the sand.
My days to too familiar, progressive for a tide, but then lost to the routine.
It was time to escape once more, to remake myself once again.

The cabin construction had set my bank account in order once more, I had means,
if only slight.  Santa Fe was known, a job was known (if not had), myself just
nin need of time still to heal, to stretch the tendons in my knee to the point
which they would mend complete. I had steeled myself, and set a date, hoping
life would accommodate itself to decisions *fait accompli*.  And thus I had
packed my tent and left the desert abode without looking back.  It was an ugly
desert not to miss, too close to modernity to be alone and too far away to
sustain some goal in life again.

We had arrived in the light day, we driving the city on a tour of memories.  The
mind lets drift memories so well, they slide into something not itself but like
through a glass darkly.  The old curving streets where I had first zipped
through town by cycle were never quite the same road, life having remade the
past in bits, small additions and subtractions, till the *ding an sich* was had
receded into the years and hid beneath so many memories of a time life was good.

Things had changed some, the coffee shop closed, my bookshop now a furniture
store. I went only once to St Johns, and could not go back.  The place was too
weird, too filled with some sense of a perfect past that I would not disturb
with the present, with the new buildings, with the new students all unknown to
me.  They would forever be unknown to me, myself the perpetual outsider now,
myself the interloper come from a world outside and known so by all.  A knit
community is as much family as barrier depending on one's relation.  I left
campus with a strange sadness sitting somewhere inside me that would keep me
away forever after.

It was not till night that we would find the old trail, I carrying that same old
duffel bag last time I lived here, mom schlepping the gray tub filled half full
of books.  I had gone soft, this time wanting something more than just the
hammock.  I would have instead a place to sit inside, a collection of things I
enjoyed and something of a spot to make my own.  We set up in a valley as
before, but this time close the edge of the forest.  Arranging my new life in
some simple way, I made the best of my tiny spot half on a hill will everything
I owned always rolling away.  We called it good enough and my mom left the next
day having helped deposit me and affairs all in the forest half a state away,
and then she headed south again, back to some semblance of normal life.  

\finish

\starbreak

The night was cold as always this time of the year, the high desert keeping to
heat for itself but giving all back to the third heaven.  Tonight the sky had a
luminous hue as the moon was only ambient behind the gathering clouds and the
slow extinguishing of stars in patches till finally a homogeneity of black
spread in all direction.  I was by this point huffing against a gathering wind
while I struggled up the hill on Katje with a bulging bags of food and water.  I
had got off work at almost midnight as usual, the city asleep and the dark well
established.  Now was only to ride up the winding roads, the ink black cut by
the wobbling shaft of an LED lamp attached to my handlebars.  Gusts of wind
would hit me sideways, the bike veering in quick corrects back and forth,
bracing for the next burst of wind.  The weather had no origin it seemed, did
not move from one place, being pushed by the atmosphere to another over the
horizon, and it was only to ride out interlude as it pushed on always to some
other place.  Santa Fe brought weather confused, a few clouds that would come
descending over Atalaya before a mass of nimbus forms were everywhere like
spontaneous generation, the gusts going in all directions at once, all jostling
and chaos.  I peddled on till I had climbed the last snaking street and topped
out at the trail head.  I locked my bike quickly while a few sprinkles began to
hit my face and I headed out and up the path.

One can always smell the rain like foreshadowing before it comes sliding down in
sheets.  There is an electric premonition in the desert air before finally the
forest will for a moment be sated.  In summer days one can feel the slowing of
time in the slow desiccating of everything, the trees quieter than normal, the
ground even mute in a silent stasis, waiting for the water to again quicken some
esoteric process of transmutation and again continue the cycles.  Only the sun
moves, day after day orbiting a world frozen for a tide, the shadows growing and
retreating endlessly and the only movement.

Then comes the rain for the first time of the season like some Jubilee to clean
the slate and wash anew the hills, a baptism from the heavens, the world will be
reborn and growing anew.  By the following day there is no sign of water except
a few dried rivulets baked into the earth where water had driven downward in a
rush continuing even after leaving the sky, yet a great exhalation is felt
afterwards from the forest.  There is a color regained, a flushed face of the
world like afterglow that is evident as I would walk though the pines.

Tonight though, the smell of rain everywhere, in the fickle wind which pushed me
in a myriad directions and sprinkled my face with a few drops as prelude.  I
struggled up faster, each step a closer point to the only shelter.  I had almost
topped out on a ridge-line which ran orthogonal to the peak when finally the
rain came.  Water came carving down,  wind making rippling
sheets which would hit me in multiple directions at once in unsigned
superposition so that all was additive.

Sheet lightening would crash horizontal somewhere in the clouds above, and for a
moment light the dark forms of trees swaying violently in some dance more
primitive than humanity.  Then another spidering hand of light would appear as
from Ares to grasp for a second the whole of heaven and boom his disapproval.  I
struggled on, wet in all ways now as I squinted against the elements. 

There is something amazing in these moments, the direct contact with something
primitively raw.  There elements impose themselves in a way that is religious, a
limit-experience that pushes itself through all the senses, opens every pore to
the moment.  Our lives are lived mostly in quotidian cutting out of ourselves,
the mind dismissing most senses and instead turning into itself, \textgreek{νοῦς
  νοήσατο},  and into abstractions.  The rain and the lightening, the cold
wind against the totality of myself, this is be fully alive.  This is to know
every part of my body all at once, an uncomfortable access to the ultimate
present.

My computer was destroyed that day, the little netbook that I would take up and
down the hill just to not leave it sitting unattended in the forest.  I would
tell myself it was silly to cart this abstruse technology into the forest each
day and back down in the morning as though I could split the difference with
modernity.  Yet I did this for over a year till finally I really got a moment
with nature, and she was not kind to my waffling with simplicity.  

\chapter{Tuktuk}
\label{cha:tuktuk}

\begin{poetry}
  She sat in stone to watch the waves\\
  and breath a sigh of froth and foam\\
  to come and take in tide and time the shore

  She would heave the rays bent low\\
  and cast a cloud with winds to blow\\
  and sit and sit and call things names no more

  She is the plane of rock of sand\\
  of hair black as where the infinite stands\\
  and from her nose her eyes her hips her hands\\
  drips words to form a world

  She is fons et origo\\
  who shivers in her creation slow\\
  tremors telluric deep and low in mysteries woman never shows\\
  and she and she alone

  She is magic in her fairy faults\\
  a crack to cleave and birth a river flow\\
  and flow till free and carve in peak and in valley\\
  a profile beautiful as her

  And thus the dove does fly\\
  silk scarf to touch a culpa by\\
  the wing to graze mountains of our lives\\
  as horizons move to merge with nothing here

  but you and I\\
  ever\\
  ever\\
  under this lilac sky
\end{poetry}

\chapter{Streetcar}
\label{cha:streetcar}

Chishimba, a name foreign and strange in my mouth.  She was all contrast, a girl
from another world that was still the same.  Zambia, New York, Hawaii, Seattle,
San Francisco, Texas, and then New Orleans, each city her blanket, a place
into which to disappear, to meld into a stream continuous.

For her the question was always of becoming, of an alchemy which would forge an
admixture like the \textgreek{ὑπόστασες} of Chalcedon which total to more than
completion.  She would be an excess of selves or be Legion and instead contain a
multitude of \textgreek{δαίμονες} and be swayed by their cacophonous cries. 

For her the past came hard in splintered selves, crystalline refractions like
myriad colors which would confuse the hue of all around.  Was there and end in
Exit when all loyalty is lost?

She would break complete the diaphanous veil and instead invent her own alembic
to clarify a lambent soul.

------

She moved in sway, some song's steps lodged permanently in her hips.  I came to
her to as student to learn her meter and keep pace the twists and turns.  

\chapter{Stairs}
\label{cha:stairs}

The old man stares blankly into the alley. Every afternoon he will be there,
metal gate open, he in the breach, dead eyes languid and incurious.  He stands
there, shirtless, belly sagging, his left foot propped on his other leg while he
looks around the tiny alley only a couple meters to the other side.  He looks
not as someone who cares to see, but instead just standing, idle, life now a
holding pattern waiting only for its culmination.

I walk past and he averts his eyes.  Three feet away now I find my gate and
fumble for my keys.  He stares past me, I always in his periphery while we both
stand there, I working angrily the lock on the gate.  We play a game of eye
contact, he skirting my gaze, I following his eyes trying to catch a glace.  The
gate finally open now, I complete my ingress with a laughing salute from behind the
bars, doff my cap and look directly, asking.  He nods ever so slightly as I turn
away, face still slack, giving finally into my persistence at the final
moment.  We will play again tomorrow. 

The boundary between inside and outside is less strict here, one flowing into
the other easily.  Doors are always open, air-conditioning rare and kept only in
the bedroom.  Drying clothes frame everything, bits of life left swaying for all
to see.  No one here is hurried, days coming on at some fixed coasting
speed. Yet everything is alive with humanity, millions of people all 
concourse with each other, each a node on some graph filled to almost solid.

There is a draw to the city that can only be felt in Asia, an emptying of the
countryside, a compacting of humanity into some tight mass.  In America, we
idealize rural life still in ways which will never let us understand the ever
growing slums of all developing countries.  Almost all those who live there
where not born in the complex systems of hovels and makeshift shelters, 
fractals of lives and ad hoc communities.  These people came here of choice, set
up their tin roofed plot and began again.  The slums never drain, for each who
makes it out, and most in time seem to, two new residents will replace them.
The slums are but a layover to a life of the city, of something less stultifying
than a shack in the country and some yearly cycle which will never change.

Saigon streets team with cars and motorbikes, the sidewalks crowded and packed.
There is seldom a place to stand out of the way while on street level, To be
outside is to be a transparent eyeball out of sheer necessity, the instinct for
self-preservation.

The first thing one has to learn to do in Vietnam is cross the street.  It
requires a confidence that does not come easily for the Occidental requiring a
faith he lost generations ago after the west was won and everyone settled down
to a middle-class life.  Here, all things moves in ways unquantifiable, a system
forever opaque in expectation and action.  Traffic is at once something one
could reasonably call a free-for-all, or in the same moment something so planned
as a minutely choreographed set of intertwined actions.  Maybe it is an emergent
system similar the human body, each cell doing its small bit until one day
sentience studies itself.  If I was to bet, higher consciousness is most likely
to exist in the network of minds on motorbikes all is some hurried mass to get
to a place somewhere else.

The city sits in a place between two worlds, one built by a generation which
knew only deprivations, poverty a constant and mobility unknown.  The city still
feels of this age, the small streets made for bicycles at best, most selling
small bits of food on their doorstep to those who wonder by or whatever they
managed to happen into.

Now modernity competes with this old world which is passing away into the
memories of a generation.  Old buildings get new shop fronts, everything painted
clean new colors while still under rusting roofs just out of sight.  Then one
day the whole building is gone and weeks later a new structure has come to take
its place among a city one can feel striving.  It is the continuous churn of
time condensed.

Yet city is slowly spacing itself out.  At the turn of the century, the density
was twice that of what it is now, a city five-fold the size.  Its landmass grows
twice as fast as the population, everyone now mobile with a machine between
their legs which can power them to a destination miles distant.

\finish{}

Like most other countries, the associated food which comes to define the cuisine
in foreign places is not the thing most eaten back at home. With Vietnam, its
two most known exports, Pho and the Banh Mi, are only a small tip of a menu so
vast as make these two items unimportant to the whole corpus.  Why is it that
counties who rely on the import of food from the world likewise only has room
for some small set of dishes?  Is it that there is no demand for the
complexities, or is it that each new restaurant only copies the one before it
until there is a self-enforce monopoly of only a select few dishes arbitrary in
origin?

\finish


\starbreak

I don't feel as though I fit in here. I pace the room wondering about the years
gone too quickly, about how they all just disappeared into some haze of
indefinite moments, recollections of people and places unconnected to here and
now.  To leave is to break with people in more ways than distance.  To explain a
new life share at no points is almost impossible.

Who comes tramping across continents to set up in a country as bizarre as
Vietnam?  Why does this city in the swelter of equatorial heat draw in those
born in the bright cities of Europe?  It must be to be out of place.

I came here to break the complacency of a normal life, of an existence easy,
set-piece, understandable.  Here is to live in the ``Uncanny Vally'', no never
be at ease with the world around, to always be on edge as though one was in the
shadow of Kafka's castle, everything sliding along in a perfect pace but forever
sideways to a person outside the internal logic.

I live now in a top hat, a room five flights up built standing alone on a
structure vertical.  Houses here are as though the shotgun of New Orleans were
turned on its side and a staircase stuck on the side.  The neighborhood is all
strings of rooms stacked and a common set of stairs gluing the whole thing
together.

The house is filled with Europeans.  Five of us climb these same steps each
day, everyone living some variant schedule that keeps us all apart.  Mostly the
stairs are empty, the dark quiet reigns, only the sticky silence of bare feet
on the tiles as I trod down to the kitchen in a descending spiral.  The kitchen
is quiet as always, a chance meeting rare.  No one cooks or cleans, everything
abundant right outside the door.

The house has the silence of a meditation, no one daring to disturb the
stillness.  The heat keeps us hidden in our rooms, tucked away from each other
in the cool of the air conditioning. All us preserved in a stasis here,
separated from something vital.

Work is too easy for most to require real investment.  A few hours a day will
pay the bills, the remaining hours a bounty of excess.  The maid comes thrice a
week to clean and wash and put everything in our lives in order.  Food arrives
for most by motorbike, ordered from bed with a handy app.  All things are easy.
Days drift by in the quiet with nothing to cling to, we all passive in our
existence, in an atmosphere of slow dissolution.

In Australia the common aches and pains of everyone, sunburned and exhausted,
cooking some poor slop and the end of the day before the heaviness of the
setting sun drew us all early to bed.  Here in the heat, we have to strains to
bind us, all our lives instead autonomous and self-contained.  Here we come as
interlopers and remain always as such, a culture and a language barrier too
broad to dissolve.

Have I come here also in dissolution?  I once more rehash my years and wonder
what the summation describes.  Spuds and I sit quiet, I scribbling and she
reading, time now for us too some abstraction.  The shadows ingress until they
take the day complete, and we will still be sitting here, another revolution in
a cycle coming unbound and instead spooling off into the aether.  I sleep in
fits, questions rife with only the vagaries of dream as answer.

My scroll grows longer, not yet long enough to contain the world, barely enough
to contain myself in outline, a mere shadow on the wall of the cave cast in
these quixotic pages.  Yet I scribble on, waiting for some moment of inspiration
to transform these lines into a whole.

\starbreak

The desire to be fixed has come recently creeping into my head.  Being here,
completely out of place, disjointed, has been clarifying.  I have made the
external anathema, and have left myself alone only with the life of my mind once
more, and I find I am not happy here alone.  It turns out, I am not a hermit who
resides only in metaphysics, but I need and want a place and reified existence.

Here I am a perverse rendition of *Desolation Angels* as Kerouac becomes slowly
insane as he looses his mind to the loneliness of the mountains, lost to the
hills up in his fire watch.  I have my own watch here, but mine a balcony
overlooking a sea of people, honking, yelling, living their lives brusquely in
an organization as foreign as the ecologies inherent to a forest.

Maybe I should have forest, have a homestead and make my way back in time to the
primitive.  I want to kill for my meat, and to know I have done so, to feel the
passing of life to make my food and feel that I am part of a chain, that I too
am but some mere moment, a generation of an absurd species which will pass again
into oblivion soon enough.

I am sure of this, one must make ones own meaning.  This is not a call to the
shallow reading of Nietzsche so given to the modern mind where our
egalitarianism requires us all to be little Ubermench, all our own civilization
extending no further than our person.  This is silliness and one should know
what is due his culture.  To adapt a phrase, ``he who knows only one society knows
no societies.''

Yet it is still for one to be creative given innate inclinations as they are.
This is what creativity consists of in essence, the creation of value, an
arbitrary assignment of all the world into a hierarchy so that all one's action
can move towards an end in \textgreek{εὐδαιμονία}.

And yet so many run around unhappy, not sure what the step before the end is, us
all in search of some system to get us a step closer, never knowing even where
we sit at the moment for most know not hell and how close is heaven.  Hayek
would have us question knowledge in markets, but this is true of life and its
vicissitudes entire, each path a flapping butterfly wing bringing hurricanes in
the future. The ground is never set either, but shifts with each step we take.
We live in a dynamic landscape in which every choice is also a shift in the
topology in which we choose, each local maxima sliding in all directions as we
make our assent trying to find our mountain tops.  And so we scramble around,
shifting this way and that, blind but for the feel of some acclivity perhaps,
some orientation toward the Good.

``Anything less than everything is never enough.'', I would recite as orison to
myself.  Yet all life is choosing, one thing had always at the cost of another.
This will forever be my discontent, that I have indeed believed my own paean to
the possible and accept nothing less.  Each place I land I attempt to cultivate
fully, yet the compromise eats away at the current and convicts me.  Unnoticed
at first, the one deprivation from some esoteric totality will grow in dimension
till it becomes subsuming to the rest.  It is a restlessness, a kind of anxious
fidgeting at the edges of each day that comes creeping in, my focus fleeing
first.  Then comes worry, a constant recounting of the years to divine the days
spent and to frantically account for the last decade and see if I have indeed
made profit of the years.  Time and deed never seem to match, one always
outpacing the other and leaving me in a despondent discord with myself and an
ephemeral possibility that seemed always over the horizon.

And so I move on always in the end, each place a mere way-point on a path whose
coordinates are still hidden, revealed each only at the last moment when there
is nothing else to do but push on.  Thus I find myself here, in Vietnam and
wondering which way time will take me next.

I  dream of the next thing, but this time a fixity.  I want a farm, a place to
indulge the desire to always innovate in every moment by a million new things
always at hand.  I want to cultivate a place, a small section of the world that
is to the extent that life will allow a creating of myself.  I have now traveled
quite a lot, and learned many things throughout my adventure, one of which is
that travel does not foist wisdom upon oneself except by adversarial
comparison.  I know many thing which I am not, some I wish to be, most I do
not.  From these, some framework emerges, an alembic set against all
possibilities which will condense and clarify what that one way should be.

\finish{}

``Self-improvement is masturbation.'', a quote well worth remembering.  The
modern self is so fixated not on necessities, but on mere accouterments, all the
``self-'' prefixed activities are in essence nothing different than an Onanistic
outburst which ends with your seed dying on the barren soil summing to less than
nothing.  Modernity wants so much to make meaning out of each life that it will
give to each a special dispensation against the mass of man, each unaware that
if given to all, there is no differentiation again.  It is the weird leveling
impulse which De Tocqueville tells of, the strange fact than all can cling so
convictedly to his individuality that the result is nothing more than a
conformity held on a level subliminal and incontestable in ways less associated
with one's essence.

And so I ask myself, why all this concern with contentment, as though it is a
thing to go out and search for.  It is probably more akin to the complexities of
meditation, such that as soon as one thinks some enlightenment is glimpsed, itn
transubstantiates itself into the *id* cloaked in fine intents all, and before
one's eyes the good becomes its contrary.  Maybe there is too much of this
aimless wondering around in search of meaning like a lost dog who has no home.
How can this be other than fad which ends only in a peacocking excess or the
depression of the discovery all is equal in the end: All die and will be
forgotten given a small window of time.  David Brooks would have us give up this
question and instead ask where we are needed.  Most are not at all either, and
have instead only an invented story of being operative in the turning of the
earth and moon. 

\finish{}

There seemed too much a reflexive pushing out of oneself into the universe in
some attempt at generating meaning only in relation.  God must have been subject
this same impulse as a complete solipsism prior to the advent of humanity.  There
was nothing but himself, subject of each sentence, all thoughts in the
middle-passive and unable to escape into a predicate which ends in an object
external.  Perfection must be in the end a bore, like Tolstoy would remind us,
``Happy families are all alike; every unhappy family is unhappy in its own
way.''.  And so he would externalize the will to create a comparison, a fallen
sort of creature who muddles through life and acts in ways irrational even to
his own interests.  His creative impulse pushes him into not less than God, a
force which generates that which did not before exist, and yet he cannot handle
this power, for meanings are the thing most difficult to create.  In the end,
even God is forgotten, and man is left to his own devices, both too powerful and
not enough to make him happy.

These are my contemplations as I scroll through Facebook in a atrabilious mood,
wondering about this new mirror of Levinas, where each is attempting to encounter
himself as the Other, an attempt at an ultimate individuation by difference in
which not to colonize the commons, but to keep in at arms length and as distinct
from the self.  Yet conformity cannot be hidden, as in the end the liberal mind
will fall into the same eddies as his comrade's. De Tocqueville was right, the
Individual goes deep into himself for the answer to all things, but because he
knows little of all, emerges with nothing but the common thought and declares it
his own.  He would have his life be his own little Athena, emerged fully formed
from his head alone to guide each act in a course unseen by the mass of men.

This is the paradox of re-posting: By definition, the thought is not one's own,
but subsidiary of the self.  Yet how better to inform the world of one's own
thoughts than the ease of the share link?  Could one encapsulate better the idea
inchoate but a moment ago then by this spiffy meme so well made?  And so the
memes propagate geometrically until everyone's individuality has been stated so
diffusely.

There is a \textit{lex non scripta} which governs each platform according to the
way by which each network is formed.  Facebook require both parties to aver a
friendship before a connection is made, while Twitter requires but a one-sided
interest.  One only ``follows'' the others mental ejaculate, little 140
character spurts which contain only enough information to signal one's stance.
Modernity has made information so abundant that most thoughts are now
commodified, bulk goods whose origin is irrelevant.  Twitter allows one to
assent to a coterie of unknown people, a kind of ephemeral caucus forever
organizing along a shifting line.

The dynamic of Facebook is different.  Each post propagates only to one's own
friends and not further, people which one has a theory of mind mixed with a
humanity for the most part.  Yet most still persist in posting thoughts which
would go unsaid in person.  There is a freedom of spatial remove which
encourages a kind of yelling into the void. Ideas too radical for a conversation
can be claimed without contest here.  For a second rule of Facebook became clear
to me only after a tide in the wilderness, which was the appropriate response to
so many ill-thought expulsions, which is to say nothing.  Offense always has the
upper hand in this land, for all are free to yell, but what makes it the void is
silence should be the response unless in a shallow agreement of the thumb
variety.  There is no conversation permitted, but instead mere statements of
self, something to be observed or seconded, but never questioned.

For this is the new age, a time of statements.  No longer to we hold our views
as such, but all becomes integral in a self-conception. All are drawn to the
necessity of obeying the imperative \textgreek{γνῶθι σεαυτόν} but the only tools
we have are to call forth phrases swirling around us like {\ae}ther.  The
frailty of such requires a protective coat of mystic affirmation which reaches
down into some soul still existent even after the death of God. Now there is an
essence composed of some smattering of a Lamarckian ``Lived Experience'' and a
quiddity bestowed by a culture long ago passed away.  Given less of systematic
understanding of Harding's Strong Objectivity, there is still something in the
air which whispers that every utterance is now a thing innate and never to be
questioned.  All now is a politics, all a symptom and cause, all a statement of
civilizational schisms.  Nothing can be an argument when all is totalizing and
nothing is merely taken any longer on its own terms.

It is so odd to feel the culture starting to slip from under oneself.  There is
a reason why we as a people have dispensed with a class of elders whom contain
the wisdom of the ages, for the ages are now in flux before our eyes, an ever
shifting set of axioms which leave the last generation suspended without
support.  Morality is a force which at once must be believed outside
temporality, and yet the history of humanity will disprove us immediately.  This
has to be held at arms length for us to assume we are the \textit{telos} of all
times, the ultimate end to a moral quest which has only taken several millions
of years.

We cannot think beyond the zeitgeist and into a future incomprehensible.  It is
only from within the system that anything is to make sense and but through a
glass darkly, everyone absolutely sure of truths which if not set in scripture
are instead made true by sheer repetition.  

Once I had a conversation with a woman in New Orleans, a girl who would rail
against the world and the means by which it has modernized; and yet she was
still as much part of the system as anyone else, supposedly hostage to something
against which her whole enlightened existence fought.  She would bike on
occasion, and if she had her was make sure China was not to modernize because it
was the path to perdition in all it's glory.

She would tell all the peasants to stay on their land and be happy in their
simplicity, that it is but our corruption that has made them envious of the city
while she herself has no choice.  She was born of the fallen, corrupt not by
nature but only by environment and without recourse to undo the actions of all
those who came before.  It is now only for us to spread the word that it is
wonderful in the new world of smart phones and internet, but like the Sirens
song will lead only to some catastrophe.


Again, symbolism seems to hold sway and dictate our actions.  Maybe the world
has just become to complex to rationalize any action, to feel out its full
consequences.  The system become subsuming, and all we have left is a few
symbolic acts.

\chapter{Thule}
\label{cha:thule}

Once again I have come back.  Back again to Santa Fe, to the same streets which
I have traversed in different lives thrice times in total.  This time I come to
find Spuds once more, one more to remake Spuds and Nug in new environs only for
that fact.

The paradox is that one hopes to return as though made anew, the product of time
and the tempering of one's rough bits one might call maturity.  One wants a kind
of alienation, for things to be fundamentally different this time.  

We came with a new car, a Honda CR-V two decades old and new to be our home.
Bed in back and Thule on top, this was to be our rebellion to adulthood still.


\starbreak{}


She pulled into the bald parking lot lodged on an indistinct street corner
surprisingly ugly for Santa Fe. The doors where always open, the smell of soap
and poverty already wafting toward the car.  Laundry mats all have a similar
feel, a confusing bit of dirtiness considering its purpose, laced with an
unspoken desperation.  Those who have to leave their house to launder their
clothes will always be of one class, and it is not those who do life well.

Inside there was already a ruckus. Two women where yelling at each other across
several lines of washing machines humming gently as though to block out the
frantically gesticulating patrons as they yelled their insults over the drone.
Something about the pandemic, as it generally was at this time.  The pandemic
was now always the vehicle of our anger, every irritable mental gesture
translated into our new language of covid, the mask some complex signaling
mechanism opaque to those less fervent.  Politics and passion where no longer
worn on our sleeve, but instead right on our face.

The yelling subsided as one of the combatant made a stompy exit and all was
again the ubiquitous white noise of cycles within cycles, wash, rinse, spin, all
in circles like the lives these machines where made to serve, 45 minutes then
dry, till next week again to wear the fibers a tiny bit once more and in the end
only threads will remain.

Spuds passed the retreating woman at the door, passing her in her huff.  Now
just a two of them, Spuds and a lone lady with furrowed brow still shoveling
clothes into a drum.  Spuds surveyed her situation as she stood with clothes
dripping from both arms and half the washers with signs stating they are
inoperable at this time, the rest it seemed whirring away already with that
manic gyration. She found a lone washer away from any unknown confrontation
tucked in a corner.  Unbundling herself, she started the next step rummaging for
the correct number of quarters when the lone woman noticed her.

Trundling over in some indefinite limp she approached Spuds from behind coming
in close enough to envelope the area with the smell of Botanical Rain reduced to
chemical compound and cigarettes that smelled of a previous generation.

Spuds wheeled around pensively, to be met with a disarmingly agreeable,
``Hello''.

``I thought I would just come warn you.  Have you seen the signs up everywhere
about the pantie bandit?''

Spuds, confused, replied, ``The pantie bandit?''

She had read the signs.  Her confusion was not the words, but this phrase uttered
from so intent a mouth, the whole face on a mission one could only guess.

``Yeah, ladies have been getting their panties stolen.  So you need to watch out
for that. Also, if some man comes up and asks you for a pair of panties, just
say no. We're working on it.''

This seemed common sense not to go giving away one's panties to strangers,
probably something her mom had warned her against growing up she was sure, even
if this particular memory elided her.

``Ok\ldots I won't\ldots don't worry.'', Spuds offered. This seemed to obliged
her assailant, who still continued standing there.

``You're\ldots working on it? You are looking for the guy?'', Spuds finally said.

``Oh we know who it is. It's my husband.  We are working on his addiction to
woman's panties.  He says he isn't stealing them any more, but is just asking
for them.   I told him its still not ok, and that he isn't allowed to come with
me to do the washing any more. But I can't watch him all the time, you know.  He
gets off and I don't know if he is down here again asking strangers for there
dirty under ware or nicking them if the place is empty.  I told him this wasn't
normal, but he just keeps it up anyhow.  One of these days the cops are gunna
get called and I'll be down giving my last cent to bail him out, so he has got
to stop it sooner or later.''

She looked some mixture of exasperated and condescendingly motherly from her
place high on moral ground.

``We talk about it and he says he stopped but then I find some new undies stuffed
in the back of drawer when I am putting away the clothes and he says they where
from before, but I know good and well they aren't.  He just can't stop himself,
but I keep telling him he has to, and one of these days maybe I will get though
to him.  We are working on it.''

The 'we' seemed rhetorical, or royal.  Spuds moved her jaw underneath her mask,
but only the sounds of washing remained as all her words have yet to congeal
around any fixed idea of what to respond.

``Oh, that's nice.'', she finally said lamely.  It was received as a matter of
course, as the woman began to barrel on about all that had gone wrong in her
marriage and the ways that she had been forced to fix so imperfect a spouse
foisted by the heavens upon her in a fit of absentmindedness.  Spuds began to
inch away as the mask of the woman bounced up and down and expelled a tale only
the universe had asked to hear.

Spuds coughed as a last attempt to illicit some kind of covid fear and cause her
too avid interlocutor to respect at least the one formality of a mid-pandemic
world, which is that of leaving strangers alone to avoid contamination.

/finish


\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%                     END DOCUMENT                      %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{poetry}
  What are the word to grasp to feel to touch a bit of this emotion I feel
  another here at hand a breath no breath really but here you are your hand to
  touch to warm too warm beside me. You are not . here where are you are but I
  still see skin my day with your body next to lie here with me and think on
  think on the world. You are cold to make me hot to make you me now just now me
  to know I am alone.
\end{poetry}






